### 2014-05-21 paper.draft.tex
Initial commit

ANNOUNCE CORRECTLY

Introduction
============
Distributed Hash Table (DHT) is a decentralized system that provides lookup services similar to hash tables; (key, values) pairs are stored in a DHT, and any particular node can efficiently retrieve the associated value. The descentralized nature and the scalability characteristics of DHT makes it the preferred way for storing shared state on P2P applications (e.g. peer lists). Kademlia and Mainline DHT are the most widley deployed DHTs world wide, creating overlay networks of milions of nodes [1].

[1] http://www.cs.helsinki.fi/u/jakangas/MLDHT/

DHTs not only serve good for storing peer swarms on P2P applications. These overlay networks are used on a high variety of Internet services. For example, CDNS [1, 2], application-level multicast, instant messaging, domain name services, web caching or distributed file systems. #TODO references for each example.

[1] Akamai
[2] Digital island

On the other hand, DHT technologies are mainly evolving thowards the Internet. However, emerging networks like Communit Networks [??] are very similar to the Internet but also have some differences.

Community Networks raise from the dramatic drop of wireless network equipement cost over the last decade which has enabled end-users to build their own network independently from traditional telecomunications providers.

Community Network infraestructure has some distinctive characteristics from the one used to power the Internet. Most of its traffic flows through short-distance, low-throughput, high-latency wireless links, build with cheap low-end hardware.

The topology characteristics of the network are also a bit different from the Internet. On village-like environments, typical CN deployment may involve a single Access Point on the top-roof of the villange which where all the clients contect to. On cities, usually the topology is a mesh-like network. Therefore, in both cases the network tends to forms clusters of nodes with a very few hops between each other but interconnected by long-distance _intervilage_ wireless links.

Locality-aware applications are much important in CN because the cost of leaving _your neighberhood cluster_ is not cheap since it may involve going through several kilometers of unreliable microwave links, with some packet loss, jitter, high latency and low throughput.

In this paper, we study the locality of DHT overlay on the context of Community Networks. In the next section background on DHT locality is presented

Background
==========
Network proximity in Distributed Hash Tables has been extensiviely studied [1, 2, 3]. Three basic approaches have been suggested for exploring proximity in DHT protocols:

i) Geographic Layout
The node IDs are assigned in a manner that ensures that nodes that are close in the network topology are close in the node ID space. Geographic Layout was explored as one technique to improve routing performance in CAN[0]. In one implementation, nodes measure the RTT between themselves and a set of landmark servers to compute the coordinates opf the node in the CAN space.

ii) Proximity Routing
The routing tables are built without taking network proximity into account but the routing algorithm chooses a nearby node at each hop from among the ones in the routing table. Proximity routing was first proposed in CAN [0]. It involves no changes to routing table construction and maintenance, because routing tables are built without taking network proximity into account. TODO complete

iii) Proximity Neighbour Selection
Routing table construction takes network proximity into account. Routing table entries are chosen to refer to nodes that are nearby in the network topology, among all live nodes with appropiate node IDs. Proximity neighbour selection is used in Tapestry and Pastry.

[0] Exploring Network Proximity
[1] LDHT

Geographic Layout techniques are very effective for building overlays with a high degree of physical locality. However, we found that in the context of community networks it may not be the best choice. Network splits are common due to both, hardware malfunction (low-end hardware used) and humman errors during management operations (difficulty of operating a descentralized network). Because of network splits a perfect locality may lead to entire portions of the DHT ID space inaccessible. In this sense Proximity routing and Proximity neighbour selection provides better reliability since the Node IDs have nothing to do with the geographic location.

Intuitively proximity routing may not work as good as Proximity neighbour selection. Because the routing table is small (compared to the total number of nodes), there is not a lot of candidates to choose from. Also priorizing pysical locality over logical locality may actually lead to an increase on the number of DHT hops when looking for a particular ID.

We think that Proximity Neighbour Selection offers the best characteristics for deployment on CN. ID space is uniformly distributed over all the network making it robust, and good enough locality can still be obtained by choosing good candidates four routing table entries.

Mainline DHT
============
We based our DHT evaluation on Mainline DHT. MLDHT is a Kademlia-based Distributed Hash Table used by BitTorrent clients to find peers via the BitTorrent protocol. MLDHT is the largest DHT network in the Internet, meassures from 2013 show from 10 million to 25 million users, with a daily churn of at least 10 million[1].

Mainline DHT protocol is very simple, limited to four control messages:

1) PING: probe a node's availability. If the node fails to respond for some time, it will be purged out of the routing table.
2) FIND_NODE: given a target ID, this message is used to find the {k} closest neighbors of the ID.
3) GET_PEERS: fiven an infohash, get the initial peer set. Notice that our evaluation is not about the bittorrent peers returned by this query.
4) ANNOUNCE_PEER: a peer announces it belongs to a swarm.

Their simplicity and the fact that is a widely deployed protocol makes its evaluation eassier, since the compleixity is low and there are several MLDHT implementations to choose from. We looked at libtorrent and PYMDHT.

libtorrent[1] was our first consideration, is a well known open source implementation of BitTorrent protocol and it has support for Mainline DHT. However, we found out that its public API provides little information about the routing state, only node IDs, not IP addresses or RTT. This is not surprising since it is mainly designed focused on BitTorrent aplications, not for routing characteristics evaluation. Also libtorrent implements a highly tunne and complicated routing algorithm with a lot of corner cases and optimizations making its behaviour less predictable[2].

    [1] http://www.rasterbar.com/products/libtorrent/
    [2] http://cs.helsinki.fi/liang.wang/publications/P2P2013_13.pdf

PYMDHT [1] is a flexible Python implementation of the Mainline DHT protocol, specifically designed for MDHT evaluation. This fact has made us choose this library over libtorrent, even though PYMDHT current state is experimental, the codebase has room for improvement and there is no documentation available.

    [1] https://github.com/rauljim/pymdht

Mainline DHT as described in Bittorrent Enhacement Proposal 5 (BEP5) [1] does not contemplate means for locality. However, implementers of this DHT are free to choose whatever routing policy they wish to. In the case of PYMDHT it supports a plugin system for this routing policy. The library ships with an implementation of a Proximity Neighbour Selection routing policy defined by NICE[2], based on RTT meassurements, which is very interesting for our locality evaluation.

    [1] http://www.bittorrent.org/beps/bep_0005.html
    [2] ???

MLDHT Locality Evaluation on Community Lab
=================
The evaluation has been performed in Community Lab [1], a Community Networks Testbed by the CONFINE project[2], is a global facility for experimentation with network technologies and services for community networks.

Interestingly, Community Lab topology has also the type of node clustering commonly seen in community network villages. In the case of Community Lab those are the nodes at UPC-Lab where only one forwarding device is between every node[1].

[1] http://monitor.confine-project.eu:8000/networktrace/

* LARGE SET OF CANDIDATE NODES

* characteristics of the MDHT
* how we can improve locality theoretically
* Why Proximity Neighbour Selection is the best approach and the others are crap
* Considterations: Small set of candidates decreases performance, size of the dht

* Even that wireless links have a lot of jitter (latency variation) we decided to use the RTT metric because it was the most feasible to use.

* Two routing policies: BEP5 vs NICE RTT (Proximity Neighbour Selection)
* Tune DHT size
* Write a simple client that:
    * Bootstrap a PYMDHT
    * Fill ID's 
    * make queries
* Routing table snapshoting
* Compare results
* CHURN

Because of the reduced number of available nodes in our testbed (in relation to the massive size of DHTs real deployments) we have found that we are not able to reproduce meaningful results of the locality characteristics of MDHT. Therefore, we have crafted our experiments intentionaly trying to ___ rather than real workload behaviours.

NUM_NODES_PER_BUCKET = 1

Not able to reduce the ID space for library limitations

High load workload
------------------
Each DHT node publishes N info hashes and perform get_peers() of all the infohashes that the other nodes have published (NUM_NODES-1)*NUM_HASHES of total queries every minute.

We made sure that the cache size of each node is large enough to hold all the IDs. Because of caching *ONE MAY EXPECT THAT* we expected data to eventually propagate to all nodes. Therefore, at some point the locality of the routing table should start to stabilize and converge to entries with low RTT (and thus more local).

*All routes

cache size: 10000 entries vs 100 entries vs cache off

Crawded bucket workload
-----------------------
All our nodes have an ID within the same bucket, and all nodes perform get_peers queries of the same infohash that is also on the same bucket.

We expect routing table entries RTT to converge to an small value

Lonely node workload
--------------------

This is a variation of the crowded bucket workload. in this case all nodes are members of the same bucket except one, that its ID belongs to the fardest bucket.

The lonley node is selected from a cluster of nodes (lab) because it has a lot of neighbors

We expected the lonely node to select a very good entry for the crowded bucket. But surprisingly the routing table remained empty, despite of the lonley node being able to send and recieve get_peers queries and responses.

Future Work
===========
* Further analysis should be performed in order to better define the locality characteristics of MLDHT.
* how does a locality-aware routing policy affects response time latency and other MDHT performance characteristics.
* meassure locality not only on the routing table (first hop), but also on the total number of hops a request goes through.
* Test with different workloads to simulate different realitstic scenarios. Different degree of simultaneous requests
* Bigger DHT size in order to perform realistic workload experiments. We haved to carefully design the scencario to test locality but if the number of nodes was bigger we ...
* Current state of tools for MDHT evaluation is not mature enough for our background and scheduled time for our project.

* Communitylab suffers from interconnection problems between community networks, also Internet connectivity is not widely available; considerably reducing the number of useful nodes. Because, nodes don't always see each other and since Internet is not always available it increases the complexity of deploying our experiment in those disconnected nodes beyond what we consider feasible for our project's schedule.
* Reasons for low number of nodes: offline, no internet and isolated, lack of public ips

Conclusions
===========
We did not proved it but improving locality on MDHT sounds theoretically plausible

Locality in MDHT seems non-existent under the analyzed workloads. Even when routing policies take into account physical information like Round trip time.

References
==========
http://dl.acm.org/citation.cfm?id=1146908

### 2014-05-21 collect.sh

@@ -1,0 +1,25 @@
+#!/bin/bash
+
+# Process de results
+#
+# USAGE:
+#   cat nodes.list | ./execute.sh "bash collect.sh"
+
+
+touch /root/routing.hops
+cat /root/routing.table | while read line; do
+    IPS=$(echo "$line" | awk {'print $3'} | grep -v '^$')
+    DISTANCES=""
+    for IP in $(echo "$IPS"|sed "s/,/ /g"); do
+        if [[ ! $(grep "$IP" /root/routing.hops) ]]; then
+            HOPS=$(traceroute -n $IP | tail -n1 | awk {'print $1'})
+            echo "$IP $HOPS" >> /root/routing.hops
+        fi
+        DISTANCES="$DISTANCES $(grep ^$IP /root/routing.hops | awk {'print $2'})"
+    done
+    HOSTNAME=$(hostname)
+    TIMESTAMP=$(echo -n "$line" | awk {'print $2'})
+    HOPS=$(echo $DISTANCES | tr ' ' ',')
+    RTTS=$(echo "$line" | awk {'print $4'} | grep -v '^$')
+    echo $HOSTNAME $TIMESTAMP $HOPS $RTTS
+done

### 2014-05-21 deploy.sh

@@ -1,0 +1,65 @@
+#!/bin/bash
+
+# Deploys experiment
+#
+# USAGE:
+#   cat nodes.list | bash deploy.sh
+#
+# REQUIRES:
+#   python get-mgmt-ips.py SLICE_ID > nodes.list
+#   cat nodes.list | bash execute.sh "ifconfig pub0|grep 'inet addr:'|cut -d':' -f2" | sed "s/ Bcast/17000/" > bootstrap_unstable
+#
+# ABORT:
+#   cat nodes.list | bash execute.sh 'pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh'
+
+
+BOOTSTRAP="10.139.40.123"
+COUNTER=0
+IDS_PER_NODE=2
+IPS=''
+
+while read IP; do
+    IPS="$IPS\n$IP"
+    COUNTER=$(($COUNTER+1))
+done
+
+IPS=$(echo "$IPS" | grep -v '^$')
+
+
+# ID[$IDS_PER_NODE*$COUNTER] = Node info hashes
+echo "
+import identifier
+for i in range($IDS_PER_NODE*$COUNTER+1):
+    print(repr(identifier.RandomId()))
+
+" | python > /tmp/infohashes.list
+
+
+# ID(0) = info_hash
+# ID(>0) = Node ID
+echo "
+import identifier
+base_ident = repr(identifier.RandomId())
+for i in range($COUNTER+2):
+    ident = repr(identifier.RandomId())
+    ident = base_ident[:30] + ident[30:]
+    print(ident)
+
+" | python > /tmp/infohashes.list
+
+
+FILES="/tmp/infohashes.list bootstrap_unstable experiment3.sh collect.sh"
+
+
+COUNTER=0
+echo -e "$IPS" | while read IP; do
+    { echo "$IP" &&
+      scp -o stricthostkeychecking=no $FILES root@[$IP]: &&
+      ssh root@$IP 'pkill -f client.py; pkill -f experiment2.sh; pkill -f experiment3.sh' ;
+      CMD="nohup bash experiment3.sh $BOOTSTRAP $COUNTER $IDS_PER_NODE" &&
+      echo "$CMD" ;
+      ssh root@$IP "$CMD" ;
+      echo "clossing ssh connection" ;
+    } &> "/tmp/exp-$COUNTER.log" &
+    COUNTER=$(($COUNTER+1))
+done

### 2014-05-21 execute.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+# Executes command on remote servers, concurrently
+#
+# USAGE:
+#   bash execute.sh "uptime"
+
+
+while read IP; do
+    echo "Querying $IP ..." 1>&2
+    ssh -o stricthostkeychecking=no root@$IP "$1" 2> /dev/null &
+done

### 2014-05-21 experiment.sh

@@ -1,0 +1,98 @@
+#!/bin/bash
+
+# Install and launch the experiment
+
+set -e
+
+BOOTSTRAP_ADDR=$1
+NODE_NUMBER=$2
+IDS_PER_NODE=$3
+
+python --version || { apt-get update && apt-get install -y --force-yes git python traceroute ; }
+
+rm -f /root/routing.table
+rm -f /tmp/got_peers.log
+rm -f /tmp/client.log
+rm -rf /root/.pymdht
+mkdir -p /root/.pymdht
+
+if [[ ! -d /root/pymdht ]]; then
+    echo "Cloning PYMDHT ..."
+    git clone https://github.com/rauljim/pymdht.git
+    cd pymdht/
+else
+    cd pymdht/
+    git reset --hard
+fi
+
+echo "Installing client ..."
+echo "
+import time
+import os
+import random
+import socket
+import struct
+
+from core import pymdht, node, identifier
+import plugins.routing_nice_rtt as r_mod
+import plugins.lookup_a4 as l_mod
+import core.exp_plugin_template as e_mod
+
+my_id = identifier.RandomId()
+my_node_info = node.Node(('0.0.0.0', 17000), my_id)
+pymdht_node = pymdht.Pymdht(my_node_info, '/root/.pymdht', r_mod, l_mod, e_mod, None, 1)
+
+def random_peer():
+    ip = socket.inet_ntoa(struct.pack('>I', random.randint(1, 0xffffffff)))
+    return (ip, 17000)
+
+def _got_peers(l_id, peers, node_):
+    with open('/tmp/got_peers.log', 'a') as log:
+        log.write(' '.join((str(peers), str(node_))))
+
+while True:
+    # Announce node IDs assigned to this NODE_NUMBER
+    with open('/root/infohashes.list', 'r') as info_file:
+        ini = $NODE_NUMBER*$IDS_PER_NODE
+        end = ($NODE_NUMBER+1)*$IDS_PER_NODE
+        for info_hash in info_file.readlines()[ini:end]:
+            info_hash = identifier.Id(info_hash.strip())
+            pymdht_node.controller._tracker.put(info_hash, random_peer())
+    
+    # Get routing table entries
+    rnodes = pymdht_node.controller._routing_m.get_main_rnodes()
+    addrs = ','.join([ rnode.addr[0] for rnode in rnodes])
[…]

### 2014-05-21 experiment2.sh

@@ -1,0 +1,107 @@
+#!/bin/bash
+
+# Install and launch the experiment
+
+set -e
+
+BOOTSTRAP_ADDR=$1
+NODE_NUMBER=$2
+IDS_PER_NODE=$3
+
+SELECTED="False"
+# 102 39
+if [[ "$NODE_NUMBER" == "39" ]]; then
+    SELECTED="True"
+fi
+python --version || { apt-get update && apt-get install -y --force-yes git python traceroute ; }
+
+rm -f /root/routing.table
+rm -f /tmp/got_peers.log
+rm -f /tmp/client.log
+rm -f /root/.pymdht/*
+mkdir -p /root/.pymdht
+
+
+if [[ ! -d /root/pymdht ]]; then
+    echo "Cloning PYMDHT ..."
+    git clone https://github.com/rauljim/pymdht.git
+    cd pymdht/
+else
+    cd pymdht/
+    git reset --hard
+fi
+
+echo "Installing client ..."
+echo "
+import time
+import os
+import random
+import socket
+import struct
+from random import randrange
+
+from core import pymdht, node, identifier
+import plugins.routing_nice_rtt as r_mod
+import plugins.lookup_a4 as l_mod
+import core.exp_plugin_template as e_mod
+
+ident = open('/root/infohashes.list', 'r').readlines()[$NODE_NUMBER+1].strip()
+selected = $SELECTED
+if selected:
+    # One selected node will have a very far ID
+    space = '0123456789abdcdef'
+    ix = space.index(ident[0])
+    #ix = (ix + (len(space)/2)) % len(space)
+    ix = (ix + 2) % len(space)
+    ident = space[ix] + ident[1:]
+
+my_id = identifier.Id(ident)
+my_node_info = node.Node(('0.0.0.0', 17000), my_id)
+pymdht_node = pymdht.Pymdht(my_node_info, '/root/.pymdht', r_mod, l_mod, e_mod, None, 1)
+
+def random_peer():
+    ip = socket.inet_ntoa(struct.pack('>I', random.randint(1, 0xffffffff)))
+    return (ip, 17000)
+
+# Announce node IDs assigned to this NODE_NUMBER
+info_hash = identifier.Id(open('/root/infohashes.list', 'r').readlines()[0].strip())
+
+def _got_peers(l_id, peers, node_):
+    with open('/tmp/got_peers.log', 'a') as log:
[…]

### 2014-05-21 experiment3.sh

@@ -1,0 +1,91 @@
+#!/bin/bash
+
+# Install and launch the experiment
+
+set -e
+
+BOOTSTRAP_ADDR=$1
+NODE_NUMBER=$2
+IDS_PER_NODE=$3
+
+python --version || { apt-get update && apt-get install -y --force-yes git python traceroute ; }
+
+rm -f /root/routing.table
+rm -f /tmp/got_peers.log
+rm -f /tmp/client.log
+rm -f /root/.pymdht/*
+mkdir -p /root/.pymdht
+
+
+if [[ ! -d /root/pymdht ]]; then
+    echo "Cloning PYMDHT ..."
+    git clone https://github.com/rauljim/pymdht.git
+    cd pymdht/
+else
+    cd pymdht/
+    git reset --hard
+fi
+
+echo "Installing client ..."
+echo "
+import time
+import os
+import random
+import socket
+import struct
+from random import randrange
+
+from core import pymdht, node, identifier
+import plugins.routing_nice_rtt as r_mod
+import plugins.lookup_a4 as l_mod
+import core.exp_plugin_template as e_mod
+
+ident = open('/root/infohashes.list', 'r').readlines()[$NODE_NUMBER+1].strip()
+my_id = identifier.Id(ident)
+my_node_info = node.Node(('0.0.0.0', 17000), my_id)
+pymdht_node = pymdht.Pymdht(my_node_info, '/root/.pymdht', r_mod, l_mod, e_mod, None, 1)
+
+def random_peer():
+    ip = socket.inet_ntoa(struct.pack('>I', random.randint(1, 0xffffffff)))
+    return (ip, 17000)
+
+# Announce node IDs assigned to this NODE_NUMBER
+info_hash = identifier.Id(open('/root/infohashes.list', 'r').readlines()[0].strip())
+
+def _got_peers(l_id, peers, node_):
+    with open('/tmp/got_peers.log', 'a') as log:
+        log.write(' '.join((str(peers), str(node_))))
+
+while True:
+    # Get routing table entries
+    rnodes = pymdht_node.controller._routing_m.get_main_rnodes()
+    addrs = ','.join([ rnode.addr[0] for rnode in rnodes])
+    rtts = ','.join([ '%.2f' % (rnode.rtt*1000) for rnode in rnodes ])
+    pid = str(os.getpid())
+    timestamp = str(time.time())
[…]

### 2014-05-21 get-mgmt-ips.py

@@ -1,0 +1,49 @@
+# Gets the management addresses of all SLICE_ID slivers
+#
+# USAGE:
+#   python get-mgmt-ips.py SLICE_ID
+#
+# REQUIRES:
+#   pip install confine-orm
+
+
+import sys
+
+from orm.api import Api
+
+
+if len(sys.argv) != 2:
+    raise AttributeError("USAGE: python get-mgmt-ips.py SLICE_ID")
+
+SLICE_ID = sys.argv[1]
+
+
+def split_len(seq, length):
+    """ Returns seq broken in a list of strings of length length """
+    return [seq[i:i+length] for i in range(0, len(seq), length)]
+
+
+def int_to_hex_str(number, digits):
+    hex_str = ('%.' + str(digits) + 'x') % number
+    err_msg = "Hex representation of %d doesn't fit in %s digits" % (number, digits)
+    assert len(hex_str) <= digits, err_msg
+    return hex_str
+
+
+def ipv6_addr(node_id, slice_id, iface_nr=2):
+    # Here we assume that mgmt iface.nr value is always 2
+    nr = '10' + int_to_hex_str(iface_nr, 2)
+    node_id = int_to_hex_str(node_id, 4)
+    slice_id = int_to_hex_str(slice_id, 12)
+    ipv6_words = MGMT_IPV6_PREFIX.split(':')[:3]
+    ipv6_words.extend([node_id, nr])
+    ipv6_words.extend(split_len(slice_id, 4))
+    return ':'.join(ipv6_words)
+
+
+controller = Api('https://controller.community-lab.net/api/')
+MGMT_IPV6_PREFIX = controller.testbed_params.mgmt_ipv6_prefix
+slivers = controller.slivers.retrieve()
+slivers.retrieve_related('node', 'slice')
+for sliver in slivers.filter(slice__id=249):
+    print(ipv6_addr(sliver.node.id, sliver.slice.id))

### 2014-05-21 graphs.py

@@ -1,0 +1,49 @@
+import glob
+
+import matplotlib.pyplot as plt
+
+
+for result in glob.glob('results/*'):
+    with open(result, 'r') as results:
+        nodes = {}
+        for line in results.readlines():
+            line = line.split()
+            if len(line) == 2:
+                node, time = line
+                hops, latencies = None, None
+            elif len(line) == 3:
+                node, time, latencies = line
+                hops = None
+            elif len(line) == 4:
+                node, time, hops, latencies = line
+            else:
+                continue
+            nodes.setdefault(node, [])
+            nodes[node].append((time, hops, latencies))
+        
+        plt.figure(1)
+        plt.title(result)
+        for node, values in nodes.iteritems():
+            node_hops = []
+            node_latencies = []
+            node_times = []
+            for value in values:
+                time, hops, latencies = value
+                time = int(time.split('.')[0])
+                node_times.append(time)
+                if hops:
+                    hops = [int(hop) for hop in hops.split(',')]
+                    hops = sum(hops)/len(hops)
+                node_hops.append(hops)
+                if latencies:
+                    latencies = [float(latency) for latency in latencies.split(',')]
+                    latencies = sum(latencies)/len(latencies)
+                node_latencies.append(latencies)
+            plt.subplot(211)
+            plt.title(result + " Hops")
+            plt.plot(node_times, node_hops)
+            plt.subplot(212)
+            plt.title(result + " Latency")
+            plt.plot(node_times, node_latencies)
+        plt.show()
+#        plt.savefig(result + '.png')

### 2014-05-21 identifier.py

@@ -1,0 +1,249 @@
+# Released under GNU LGPL 2.1
+# See LICENSE.txt for more information
+
+"""
+This module provides the Id object and necessary tools.
+
+"""
+
+#binascii.hexlify() bin>hex
+#int(a, 16) hex>int
+#hex() int>hex
+
+import sys
+import random
+import base64
+
+import logging
+
+logger = logging.getLogger('dht')
+
+
+BITS_PER_BYTE = 8
+ID_SIZE_BYTES = 20 # This has been changed (default: 20)
+ID_SIZE_BITS = ID_SIZE_BYTES * BITS_PER_BYTE
+MAX_ID_LONG = ALL_ONES_LONG = (1 << ID_SIZE_BITS) - 1
+
+class IdError(Exception):
+    pass
+
+
+class Id(object):
+
+    """Convert a string to an Id object.
+    The bin_id string's lenght must be ID_SIZE bytes (characters)
+    OR an integer/long.
+
+    You can use both binary and hexadecimal strings. Example:
+    
+    >>> Id(chr(0) * ID_SIZE_BYTES) == Id('0' * ID_SIZE_BYTES * 2)
+    True
+    
+    >>> Id(chr(255) * ID_SIZE_BYTES) == Id('f' * ID_SIZE_BYTES * 2)
+    True
+
+    >>> Id(chr(0) * ID_SIZE_BYTES) == Id(0)
+    True
+
+    >>> Id(chr(255) * ID_SIZE_BYTES) == Id(MAX_ID_LONG)
+    True
+    
+    """
+
+    def __init__(self, hex_or_bin_id):
+        self._bin_id = None
+        self._bin = None
+        self._hex = None
+        self._bin_str = None
+        self._long = None
+        self._log = None
+        if isinstance(hex_or_bin_id, str):
+            if len(hex_or_bin_id) == ID_SIZE_BYTES:
+                self._bin_id = hex_or_bin_id
+            elif len(hex_or_bin_id) == ID_SIZE_BYTES*2:
+                self._hex = hex_or_bin_id
+                try:
+                    self._bin_id = base64.b16decode(hex_or_bin_id, True)
+                except:
+                    raise IdError, 'input: %r' % hex_or_bin_id
+        elif isinstance(hex_or_bin_id, long) or isinstance(hex_or_bin_id, int):
+            if hex_or_bin_id < 0 or hex_or_bin_id > MAX_ID_LONG:
[…]

### 2014-05-21 paper.draft.tex
paper draft

@@
 ============
-Distributed Hash Table (DHT) is a decentralized system that provides lookup services similar to hash tables; (key, values) pairs are stored in a DHT, and any particular node can efficiently retrieve the associated value.
-The descentralized nature and the scalability characteristics of DHT makes it the preferred way for storing shared state on P2P applications (e.g.
-peer lists).
-Kademlia and Mainline DHT are the most widley deployed DHTs world wide, creating overlay networks of milions of nodes [1].
+Distributed Hash Table (DHT) is a decentralized system that provides lookup services 
+similar to hash tables; (key, values) pairs are stored in a DHT, and any particular 
+node can efficiently retrieve the associated value. The descentralized nature and 
+the scalability characteristics of DHT makes it the preferred way for storing shared 
+state on P2P applications (e.g. peer lists). Kademlia and Mainline DHT are the most 
+widley deployed DHTs world wide, creating overlay networks of milions of nodes [1].
 
@@
 
-DHTs not only serve good for storing peer swarms on P2P applications.
-These overlay networks are used on a high variety of Internet services.
-For example, CDNS [1, 2], application-level multicast, instant messaging, domain name services, web caching or distributed file systems.
-#TODO references for each example.
+However, DHTs not only serve good for storing peer swarms on P2P applications. These overlay 
+networks are used on a large variety of Internet services. For example, CDNS [1, 2], 
+application-level multicast, instant messaging, domain name services, web caching 
+or distributed file systems. #TODO references for each example.
 
@@
 
-On the other hand, DHT technologies are mainly evolving thowards the Internet. However, emerging networks like Communit Networks [??] are very similar to the Internet but also have some differences.
+On the other hand, DHT technologies are mainly evolving thowards the Internet. 
+Even though emerging networks like Communit Networks [??] are based on the same 
+fundamental technology than Internet, they also have their own differences and peculiarities.
 
-Community Networks raise from the dramatic drop of wireless network equipement cost over the last decade which has enabled end-users to build their own network independently from traditional telecomunications providers.
-
-Community Network infraestructure has some distinctive characteristics from the one used to power the Internet.
-Most of its traffic flows through short-distance, low-throughput, high-latency wireless links, build with cheap low-end hardware.
+Community Networks raise from the dramatic drop of wireless network equipement 
+cost over the last decade which has enabled end-users to build their own network 
+independently from traditional telecomunications providers. This has a dramatic 
+impact on the network properties. Most of its traffic flows through short-distance, 
+low-throughput, high-latency wireless links, build with cheap low-end hardware.
 
 The topology characteristics of the network are also a bit different from the Internet. 
-On village-like environments, typical CN deployment may involve a single Access Point on the top-roof of the villange which where all the clients contect to.
-On cities, usually the topology is a mesh-like network.
-Therefore, in both cases the network tends to forms clusters of nodes with a very few hops between each other but interconnected by long-distance _intervilage_ wireless links.
+On village-like environments, typical CN deployment may involve a single Access Point 
+on the top-roof of the villange from which all the clients contect to. On cities, 
+usually the topology is a mesh-like network. Therefore, in both cases the network 
+tends to forms clusters of nodes with a very few hops between each other but interconnected 
+by long-distance intervilage wireless links.
 
-Locality-aware applications are much important in CN because the cost of leaving _your neighberhood cluster_ is not cheap since it may involve going through several kilometers of unreliable microwave links, with some packet loss, jitter, high latency and low throughput.
+Locality-aware applications become much important in CN because the cost of leaving 
+_your neighberhood cluster_ is particularly expensive since it may involve going 
+through several kilometers of unreliable microwave links, with more packet loss, 
+more jitter, higher latency and lower throughput.
 
-In this paper, we study the locality of DHT overlay on the context of Community Networks. In the next section background on DHT locality is presented
+In this paper, we study the locality of DHT overlay on the context of Community 
+Networks. In the next section background on DHT locality is presented.
 
@@
 ==========
-Network proximity in Distributed Hash Tables has been extensiviely studied [1, 2, 3]. Three basic approaches have been suggested for exploring proximity in DHT protocols:
+Network proximity (locality) in Distributed Hash Tables has been extensiviely studied [1, 2, 3]. 
+Three basic approaches have been suggested for exploring proximity in DHT protocols:
 
 i) Geographic Layout
-The node IDs are assigned in a manner that ensures that nodes that are close in the network topology are close in the node ID space.
-Geographic Layout was explored as one technique to improve routing performance in CAN[0].
-In one implementation, nodes measure the RTT between themselves and a set of landmark servers to compute the coordinates opf the node in the CAN space.
+The node IDs are assigned in a manner that ensures that nodes that are close in the 
+network topology are close in the node ID space. Geographic Layout was explored as 
+one technique to improve routing performance in CAN[0]. In one implementation, 
+nodes measure the RTT between themselves and a set of landmark servers to compute 
+the coordinates opf the node in the CAN space.
 
 ii) Proximity Routing
-The routing tables are built without taking network proximity into account but the routing algorithm chooses a nearby node at each hop from among the ones in the routing table.
-Proximity routing was first proposed in CAN [0].
-It involves no changes to routing table construction and maintenance, because routing tables are built without taking network proximity into account.
-TODO complete
+The routing tables are built without taking network proximity into account but the 
+routing algorithm chooses a nearby node at each hop from among the ones in the 
+routing table. Proximity routing was first proposed in CAN [0]. It involves no 
+changes to routing table construction and maintenance, because routing tables are 
+built without taking network proximity into account. TODO complete
 
 iii) Proximity Neighbour Selection
-Routing table construction takes network proximity into account.
-Routing table entries are chosen to refer to nodes that are nearby in the network topology, among all live nodes with appropiate node IDs.
-Proximity neighbour selection is used in Tapestry and Pastry.
+Routing table construction takes network proximity into account. Routing table 
+entries are chosen to refer to nodes that are nearby in the network topology, 
+among all live nodes with appropiate node IDs. Proximity neighbour selection is 
+used in Tapestry and Pastry.
 
@@
 
-Geographic Layout techniques are very effective for building overlays with a high degree of physical locality.
-However, we found that in the context of community networks it may not be the best choice.
-Network splits are common due to both, hardware malfunction (low-end hardware used) and humman errors during management operations (difficulty of operating a descentralized network).
-Because of network splits a perfect locality may lead to entire portions of the DHT ID space inaccessible.
-In this sense Proximity routing and Proximity neighbour selection provides better reliability since the Node IDs have nothing to do with the geographic location.
+Geographic Layout techniques are very effective for building overlays with a 
+high degree of physical locality. However, we found that in the context of 
+community networks it may not be the best choice. Network splits are common due to both, 
+hardware malfunction (low-end hardware used) and humman errors during management 
+operations (difficulty of operating a highly descentralized network). Because of network 
+splits a perfect locality may lead to entire portions of the DHT ID space inaccessible. 
+In this sense, Proximity Routing and Proximity Neighbour Selection provides much better 
+reliability since the Node IDs have nothing to do with the geographic location.
 
-Intuitively proximity routing may not work as good as Proximity neighbour selection.
-Because the routing table is small (compared to the total number of nodes), there is not a lot of candidates to choose from.
-Also priorizing pysical locality over logical locality may actually lead to an increase on the number of DHT hops when looking for a particular ID.
+Intuitively Proximity Routing may not work as good as Proximity Neighbour Selection. 
+Because the routing table is small (compared to the total number of nodes), there 
+are not a lot of candidates to choose from. Also priorizing pysical locality over 
+logical locality may actually lead to an increase on the number of DHT hops for 
+lookup operations.
 
-We think that Proximity Neighbour Selection offers the best characteristics for deployment on CN.
-ID space is uniformly distributed over all the network making it robust, and good enough locality can still be obtained by choosing good candidates four routing table entries.
+We believe that Proximity Neighbour Selection offers the best characteristics for 
+deployment on CN. ID space is uniformly distributed over the whole network, making 
+it robust, while good enough locality can still be achieved by choosing good candidates 
+as routing table entries.
 
@@
 ============
-We based our DHT evaluation on Mainline DHT.
-MLDHT is a Kademlia-based Distributed Hash Table used by BitTorrent clients to find peers via the BitTorrent protocol.
-MLDHT is the largest DHT network in the Internet, meassures from 2013 show from 10 million to 25 million users, with a daily churn of at least 10 million[1].
+We based our DHT evaluation on Mainline DHT (MLDHT). MLDHT is a Kademlia-based 
+Distributed Hash Table used by BitTorrent clients to find peers via the BitTorrent 
+protocol. MLDHT is the largest DHT network in the Internet, meassures from 2013 
+show from 10 million to 25 million users, with a daily churn of at least 10 million[1].
 
-Mainline DHT protocol is very simple, limited to four control messages:
+Mainline DHT protocol is actually pretty simple, limited to four control messages:
 
-1) PING: probe a node's availability. If the node fails to respond for some time, it will be purged out of the routing table.
+1) PING: probe a node's availability. If the node fails to respond for some time, 
+    it will be purged out of the routing table.
 2) FIND_NODE: given a target ID, this message is used to find the {k} closest neighbors of the ID.
-3) GET_PEERS: fiven an infohash, get the initial peer set. Notice that our evaluation is not about the bittorrent peers returned by this query.
+3) GET_PEERS: fiven an infohash, get the initial peer set. Notice that our evaluation 
+    is not about the bittorrent peers returned by this query.
 4) ANNOUNCE_PEER: a peer announces it belongs to a swarm.
 
-Their simplicity and the fact that is a widely deployed protocol makes its evaluation eassier, since the compleixity is low and there are several MLDHT implementations to choose from.
-We looked at libtorrent and PYMDHT.
+Its simplicity and the fact that it is a widely deployed protocol makes its evaluation 
+study somehow eassier, since the compleixity is low and there are several MLDHT 
+implementations to choose from. We looked at libtorrent and PYMDHT.
 
-libtorrent[1] was our first consideration, is a well known open source implementation of BitTorrent protocol and it has support for Mainline DHT.
-However, we found out that its public API provides little information about the routing state, only node IDs, not IP addresses or RTT.
-This is not surprising since it is mainly designed focused on BitTorrent aplications, not for routing characteristics evaluation.
-Also libtorrent implements a highly tunne and complicated routing algorithm with a lot of corner cases and optimizations making its behaviour less predictable[2].
+libtorrent[1] was our first consideration, is a well known open source implementation 
+of BitTorrent protocol and it has support for Mainline DHT. However, we quickly found out 
+that its public API provides little information about the DHT routing state, only 
+providing the node ID of its entrie, not IP addresses or RTT. This is not surprising since its designe is 
+focused on BitTorrent aplications, not on DHT routing characteristics evaluation. 
+Also libtorrent implements a highly tunne and complicated routing algorithm with a 
+lot of corner cases and optimizations making its behaviour less predictable[2].
 
@@
 
-PYMDHT [1] is a flexible Python implementation of the Mainline DHT protocol, specifically designed for MDHT evaluation.
-This fact has made us choose this library over libtorrent, even though PYMDHT current state is experimental, the codebase has room for improvement and there is no documentation available.
+PYMDHT [1] is a flexible Python implementation of the Mainline DHT protocol, 
+specifically designed for MDHT evaluation. This fact has made us choose this 
+library over libtorrent. Even though PYMDHT current state is experimental, 
+the codebase has room for improvement and there is no public documentation available.
 
@@
 
-Mainline DHT as described in Bittorrent Enhacement Proposal 5 (BEP5) [1] does not contemplate means for locality.
-However, implementers of this DHT are free to choose whatever routing policy they wish to.
-In the case of PYMDHT it supports a plugin system for this routing policy.
-The library ships with an implementation of a Proximity Neighbour Selection routing policy defined by NICE[2], based on RTT meassurements, which is very interesting for our locality evaluation.
+Mainline DHT as described in Bittorrent Enhacement Proposal 5 (BEP5) [1] does not 
+contemplate means for locality. However, implementers of this DHT are free to choose 
+whatever routing policy they wish to. In the case of PYMDHT it supports a plugin system 
+for the routing policy. The library ships with an implementation of a Proximity Neighbour 
+Selection routing policy defined by NICE[2], based on RTT meassurements, which 
+is very interesting for our locality evaluation.
 
@@
 MLDHT Locality Evaluation on Community Lab
-=================
-The evaluation has been performed in Community Lab [1], a Community Networks Testbed by the CONFINE project[2], is a global facility for experimentation with network technologies and services for community networks.
+==========================================
+The evaluation has been performed in Community Lab [1], a Community Networks Testbed 
+by the CONFINE project[2], is a global facility for experimentation with network 
+technologies and services for community networks.
 
-Interestingly, Community Lab topology has also the type of node clustering commonly seen in community network villages.
-In the case of Community Lab those are the nodes at UPC-Lab where only one forwarding device is between every node[1].
+Interestingly, Community Lab topology has also the type of node clustering commonly 
+seen in community network villages. In the case of Community Lab those are the nodes 
+at UPC-Lab where only one forwarding device sits between every node[1].
 
@@
 
-* Even that wireless links have a lot of jitter (latency variation) we decided to use the RTT metric because it was the most feasible to use.
+* Even that wireless links have a lot of jitter (latency variation) we decided to 
+use the RTT metric because it was the most feasible to use.
 
@@
 
-Because of the reduced number of available nodes in our testbed (in relation to the massive size of DHTs real deployments) we have found that we are not able to reproduce meaningful results of the locality characteristics of MDHT.
-Therefore, we have crafted our experiments intentionaly trying to ___ rather than real workload behaviours.
+Because of the reduced number of available nodes in our testbed (in relation to 
+the massive DHT size in real deployments) we have found that we are not able to 
+reproduce meaningful results of the locality characteristics of MLDHT. 
+Therefore, we have crafted some workloads trying to artificaly promote locality 
+rather than focus on real workload behaviours.
 
@@
 ------------------
-Each DHT node publishes N info hashes and perform get_peers() of all the infohashes that the other nodes have published (NUM_NODES-1)*NUM_HASHES of total queries every minute.
+Each DHT node publishes N info hashes and perform get_peers() of all the infohashes 
+that the other nodes have published (NUM_NODES-1)*NUM_HASHES of total queries every minute.
 
 We made sure that the cache size of each node is large enough to hold all the IDs. 
-Because of caching *ONE MAY EXPECT THAT* we expected data to eventually propagate to all nodes.
-Therefore, at some point the locality of the routing table should start to stabilize and converge to entries with low RTT (and thus more local).
+Because of caching *ONE MAY EXPECT THAT* we expected data to eventually propagate 
+to all nodes. Therefore, at some point the locality of the routing table should start 
+to stabilize and converge to entries with low RTT (and thus more local).
 
@@
 -----------------------
-All our nodes have an ID within the same bucket, and all nodes perform get_peers queries of the same infohash that is also on the same bucket.
+All our nodes have an ID within the same bucket, and all nodes perform get_peers 
+queries of the same infohash that is also on the same bucket.
 
@@
 
-This is a variation of the crowded bucket workload. in this case all nodes are members of the same bucket except one, that its ID belongs to the fardest bucket.
+This is a variation of the crowded bucket workload. in this case all nodes are 
+members of the same bucket except one, that its ID belongs to the fardest bucket.
 
@@
 We expected the lonely node to select a very good entry for the crowded bucket. 
-But surprisingly the routing table remained empty, despite of the lonley node being able to send and recieve get_peers queries and responses.
+But surprisingly the routing table remained empty, despite of the lonley node being 
+able to send and recieve get_peers queries and responses.
 
@@
 Because, nodes don't always see each other and since Internet is not always available it increases the complexity of deploying our experiment in those disconnected nodes beyond what we consider feasible for our project's schedule.
-* Reasons for low number of nodes: offline, no internet and isolated, lack of public ips
+* Reasons for low number of nodes: offline, no Internet and isolated, lack of CN public ips
 
@@
 
+Naive changes on the routing table policy in order to improve locality may actually 
+harm locality because of the nature of the MLDHT. More hops? disrupt logical locality?
+
 References

### 2014-05-21 paper.draft.tex
paper draft

@@
 
-The topology characteristics of the network are also a bit different from the Internet. 
+The topology characteristics of the network are also a bit different from the traditional Internet. 
 On village-like environments, typical CN deployment may involve a single Access Point 
@@
 _your neighberhood cluster_ is particularly expensive since it may involve going 
-through several kilometers of unreliable microwave links, with more packet loss, 
-more jitter, higher latency and lower throughput.
+through several kilometers of unreliable microwave links, with significative packet loss, 
+jitter, high latency and low throughput.
 
-In this paper, we study the locality of DHT overlay on the context of Community 
+In this paper, we study the locality characteristics of DHT overlay on the context of Community 
 Networks. In the next section background on DHT locality is presented.

### 2014-05-21 paper.draft.tex
paper draft

@@
 operations (difficulty of operating a highly descentralized network). Because of network 
-splits a perfect locality may lead to entire portions of the DHT ID space inaccessible. 
+splits, a perfect locality based on Geographic Layout may lead to entire portions of the DHT ID space inaccessible. 
 In this sense, Proximity Routing and Proximity Neighbour Selection provides much better 
@@
 deployment on CN. ID space is uniformly distributed over the whole network, making 
-it robust, while good enough locality can still be achieved by choosing good candidates 
+it robust, while good enough locality can still be achieved by choosing nearby nodes  
 as routing table entries.

### 2014-05-22 deploy.sh
added split nodes and imporved graphs with LR

@@ -3,7 +3,7 @@
 # Deploys experiment
 #
 # USAGE:
-#   cat nodes.list | bash deploy.sh
+#   cat nodes.list | bash deploy.sh EXPNUM
 #
 # REQUIRES:
 #   python get-mgmt-ips.py SLICE_ID > nodes.list
@@ -15,8 +15,9 @@
 
 BOOTSTRAP="10.139.40.123"
 COUNTER=0
-IDS_PER_NODE=2
+IDS_PER_NODE=1
 IPS=''
+EXPNUM=$1
 
 while read IP; do
     IPS="$IPS\n$IP"
@@ -45,18 +46,18 @@ for i in range($COUNTER+2):
     ident = base_ident[:30] + ident[30:]
     print(ident)
 
-" | python > /tmp/infohashes.list
+" | python > /tmp/infohashes2.list
 
 
-FILES="/tmp/infohashes.list bootstrap_unstable experiment3.sh collect.sh"
+FILES="/tmp/infohashes.list bootstrap_unstable experiment$EXPNUM.sh collect.sh"
 
 
 COUNTER=0
 echo -e "$IPS" | while read IP; do
     { echo "$IP" &&
       scp -o stricthostkeychecking=no $FILES root@[$IP]: &&
-      ssh root@$IP 'pkill -f client.py; pkill -f experiment2.sh; pkill -f experiment3.sh' ;
-      CMD="nohup bash experiment3.sh $BOOTSTRAP $COUNTER $IDS_PER_NODE" &&
+      ssh root@$IP 'pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh' ;
+      CMD="nohup bash experiment$EXPNUM.sh $BOOTSTRAP $COUNTER $IDS_PER_NODE" &&
       echo "$CMD" ;
       ssh root@$IP "$CMD" ;
       echo "clossing ssh connection" ;

### 2014-05-22 experiment.sh

@@ -68,7 +68,7 @@ while True:
     # Log routing table entries
     with open('/root/routing.table', 'a') as log:
         log.write(' '.join((pid, timestamp, addrs, rtts)) + '\n')
-    time.sleep(50)
+    time.sleep(random.randrange(60, 300))
     # Make queries to all IDs
     with open('/root/infohashes.list', 'r') as info_file:
         for info_hash in info_file.readlines():
@@ -80,9 +80,9 @@ echo "Patching pymdht..."
 # try to prevent minitwisted to crash when address is unreachable ...
 sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnets.remove(utils.get_subnet(addr))\n        except KeyError: pass/" core/bootstrap.py
 # Adapt bucket dimensioning to our DHT small size
-sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 2/" plugins/routing_nice_rtt.py
+sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/" core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 1/" core/tracker.py
 # Change routing policy
 sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-22 graphs.py

@@ -1,11 +1,21 @@
 import glob
+import sys
 
 import matplotlib.pyplot as plt
+import numpy as np
+from pylab import plot,show
 
 
-for result in glob.glob('results/*'):
+FILES = '*'
+if len(sys.argv) == 2:
+    FILES = sys.argv[1]
+
+
+for result in glob.glob('results/' + FILES):
+    initial_time = None
     with open(result, 'r') as results:
         nodes = {}
+        times = {}
         for line in results.readlines():
             line = line.split()
             if len(line) == 2:
@@ -13,13 +23,22 @@ for result in glob.glob('results/*'):
                 hops, latencies = None, None
             elif len(line) == 3:
                 node, time, latencies = line
+                latencies = [float(latency) for latency in latencies.split(',')]
                 hops = None
             elif len(line) == 4:
                 node, time, hops, latencies = line
+                hops = [int(hop) for hop in hops.split(',')]
+                latencies = [float(latency) for latency in latencies.split(',')]
             else:
                 continue
+            
             nodes.setdefault(node, [])
+            time = int(time.split('.')[0])
             nodes[node].append((time, hops, latencies))
+            
+            key = int(str(time)[:-2] + '00')
+            times.setdefault(key, [])
+            times[key].append((time, hops, latencies))
         
         plt.figure(1)
         plt.title(result)
@@ -29,21 +48,46 @@ for result in glob.glob('results/*'):
             node_times = []
             for value in values:
                 time, hops, latencies = value
-                time = int(time.split('.')[0])
                 node_times.append(time)
                 if hops:
-                    hops = [int(hop) for hop in hops.split(',')]
                     hops = sum(hops)/len(hops)
                 node_hops.append(hops)
                 if latencies:
-                    latencies = [float(latency) for latency in latencies.split(',')]
                     latencies = sum(latencies)/len(latencies)
                 node_latencies.append(latencies)
-            plt.subplot(211)
+            plt.subplot(311)
             plt.title(result + " Hops")
             plt.plot(node_times, node_hops)
-            plt.subplot(212)
+            plt.subplot(312)
             plt.title(result + " Latency")
             plt.plot(node_times, node_latencies)
+        
+        t_result, h_result, l_result = [], [], []
+        for time, values in times.iteritems():
+            time_hops = []
+            time_latencies = []
+            for value in values:
[…]

### 2014-05-22 split-nodes.py

@@ -1,0 +1,21 @@
+#!/bin/python
+
+# USAGE:
+#   python split-nodes.py 3 0 | bash deploy.sh
+
+
+import sys
+
+
+if len(sys.argv) == 1:
+    SPLIT = False
+else:
+    SPLIT = True
+    MOD = int(sys.argv[1])
+    CUR = int(sys.argv[2])
+
+
+with open('nodes.list', 'r') as nodes:
+    for ix, line in enumerate(nodes.readlines()):
+        if not SPLIT or ix % MOD == CUR:
+            print line.strip()

### 2014-05-22 conductor.sh
Added results

@@ -1,0 +1,11 @@
+python split-nodes.py 3 0 | bash deploy.sh
+sleep $((20*60))
+python split-nodes.py 3 1 | bash deploy.sh
+sleep $((20*60))
+python split-nodes.py 3 2 | bash deploy.sh
+sleep $((20*60))
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 10
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 100
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-ids1-cache10000000

### 2014-05-22 experiment.sh

@@ -82,7 +82,7 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 1/" core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/" core/tracker.py
 # Change routing policy
 sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-22 graphs.py

@@ -77,17 +77,18 @@ for result in glob.glob('results/' + FILES):
             if time_hops:
                 t_result.append(time)
                 h_result.append(sum(time_hops)/len(time_hops) if time_hops else None)
-                l_result.append(sum(time_latencies)/len(time_latencies)/10 if time_latencies else None)
-        plt.subplot(313)
-        plt.title(result + " Slotted")
+                l_result.append(sum(time_latencies)/len(time_latencies)/20 if time_latencies else None)
         
         xi = np.array(t_result)
         xi = np.array(t_result)
         A = np.array([ xi, np.ones(len(xi))])
         y = np.array(h_result, dtype=np.float)
         y = np.ma.masked_array(y, np.isnan(y))
-        w = np.linalg.lstsq(A.T,y)[0] # obtaining the parameters
-        line = w[0]*xi+w[1] # regression line
+        w = np.linalg.lstsq(A.T,y)[0]
+        line = w[0]*xi+w[1]
+        
+        plt.subplot(313)
+        plt.title(result + " Slotted")
         plt.plot(t_result, h_result, 'g^', t_result, l_result, 'bs', t_result, line,'g-', )
         plt.show()
 #        plt.savefig(result + '.png')

### 2014-05-22 conductor.sh
Exp

@@ -8,4 +8,4 @@ python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment
 sleep 10
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 100
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-ids1-cache10000000
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-ids1-cache1

### 2014-05-22 experiment.sh

@@ -82,7 +82,7 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/" core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 1/" core/tracker.py
 # Change routing policy
 sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-22 conductor.sh
conductor

@@ -1,3 +1,7 @@
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 10
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 200
 python split-nodes.py 3 0 | bash deploy.sh
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh
@@ -8,4 +12,116 @@ python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment
 sleep 10
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 100
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-ids1-cache10000000
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp1-ids1-cache100
+
+sleep 300
+
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 10
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 200
+python split-nodes.py 3 0 | bash deploy.sh 2
+sleep $((20*60))
+python split-nodes.py 3 1 | bash deploy.sh 2
+sleep $((20*60))
+python split-nodes.py 3 2 | bash deploy.sh 2
+sleep $((20*60))
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 10
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 100
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp2-cache100-node39
+
+sleep 300
+
[…]

### 2014-05-22 deploy.sh

@@ -47,6 +47,8 @@ for i in range($COUNTER+2):
     print(ident)
 
 " | python > /tmp/infohashes2.list
+cp /tmp/infohashes2.list /tmp/infohashes3.list
+cp /tmp/infohashes$EXPNUM.list /tmp/infohashes.list
 
 
 FILES="/tmp/infohashes.list bootstrap_unstable experiment$EXPNUM.sh collect.sh"

### 2014-05-22 experiment.sh

@@ -82,7 +82,7 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/" core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 100/" core/tracker.py
 # Change routing policy
 sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-22 conductor.sh
merge

@@ -1,7 +1,6 @@
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 10
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 200
+
 python split-nodes.py 3 0 | bash deploy.sh
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh
@@ -9,17 +8,11 @@ sleep $((20*60))
 python split-nodes.py 3 2 | bash deploy.sh
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 10
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 100
+sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp1-ids1-cache100
 
 sleep 300
 
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 10
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 200
 python split-nodes.py 3 0 | bash deploy.sh 2
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh 2
@@ -27,17 +20,11 @@ sleep $((20*60))
 python split-nodes.py 3 2 | bash deploy.sh 2
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 10
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 100
+sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp2-cache100-node39
 
[…]

### 2014-05-22 conductor.sh
conductor

@@ -98,3 +98,61 @@ sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp1-ids10-cache10000000
+
+
+##########################
+##########################
+
+sleep 200
+sed -i 's#10000000/" #100/"#' experiment.sh
+sed -i "s/IDS_PER_NODE=10/IDS_PER_NODE=1/" deploy.sh
+python split-nodes.py | bash deploy.sh
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-ids1-cache100
+
+sleep 300
+
+sed -i 's/"102"/"39"/' experiment2.sh
+python split-nodes.py | bash deploy.sh 2
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp2-cache100-node39
+
+sleep 300
+
+python split-nodes.py | bash deploy.sh 3
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp3-cache100
+
+sleep 300
+
+sed -i "s/IDS_PER_NODE=1/IDS_PER_NODE=2/" deploy.sh
+python split-nodes.py | bash deploy.sh
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-ids2-cache100
+
+sleep 300
+
+sed -i "s/IDS_PER_NODE=2/IDS_PER_NODE=10/" deploy.sh
+python split-nodes.py | bash deploy.sh
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-ids10-cache100
+
+sleep 300
+
+sed -i 's/"39"/"102"/' experiment2.sh
+python split-nodes.py | bash deploy.sh 2
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp2-cache100-node102
+
+sleep 300
+
+python split-nodes.py | bash deploy.sh 3
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp3-cache100-2
+
+sleep 300
+
+sed -i 's#100/" #10000000/"#' experiment.sh
[…]

### 2014-05-22 graphs.py

@@ -89,6 +89,6 @@ for result in glob.glob('results/' + FILES):
         
         plt.subplot(313)
         plt.title(result + " Slotted")
-        plt.plot(t_result, h_result, 'g^', t_result, l_result, 'bs', t_result, line,'g-', )
+        plt.plot(t_result, h_result, 'g^', t_result, l_result, 'bs', t_result, line,'g-')
         plt.show()
 #        plt.savefig(result + '.png')

### 2014-05-22 conductor.sh
conductr

@@ -1,68 +1,75 @@
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 200
+source utils.sh
 
-python split-nodes.py 3 0 | bash deploy.sh
+COUNTER=$(wc -l nodes.list|awk {'print $1'})
+
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 200
+gen_ids $COUNTER 1
+python split-nodes.py 3 0 | bash deploy.sh 1 1
 sleep $((20*60))
-python split-nodes.py 3 1 | bash deploy.sh
+python split-nodes.py 3 1 | bash deploy.sh 1 1
 sleep $((20*60))
-python split-nodes.py 3 2 | bash deploy.sh
+python split-nodes.py 3 2 | bash deploy.sh 1 1
 sleep $((20*60))
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp1-ids1-cache100
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-churn3-ids1-cache100
 
 sleep 300
 
+gen_close_ids $COUNTER
 python split-nodes.py 3 0 | bash deploy.sh 2
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh 2
 sleep $((20*60))
 python split-nodes.py 3 2 | bash deploy.sh 2
 sleep $((20*60))
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
[…]

### 2014-05-22 deploy.sh

@@ -3,62 +3,29 @@
 # Deploys experiment
 #
 # USAGE:
-#   cat nodes.list | bash deploy.sh EXPNUM
+#   cat nodes.list | bash deploy.sh [EXPNUM] [IDS_PER_NODE]
 #
 # REQUIRES:
 #   python get-mgmt-ips.py SLICE_ID > nodes.list
 #   cat nodes.list | bash execute.sh "ifconfig pub0|grep 'inet addr:'|cut -d':' -f2" | sed "s/ Bcast/17000/" > bootstrap_unstable
+#   . utils.sh; gen_ids $(wc -l nodes.list|awk {'print $1'}) IDS_PER_NODE
 #
 # ABORT:
 #   cat nodes.list | bash execute.sh 'pkill -f client.py; pkill -f experiment.sh; pkill -f experiment2.sh'
 
 
 BOOTSTRAP="10.139.40.123"
-COUNTER=0
-IDS_PER_NODE=1
-IPS=''
-EXPNUM=$1
-
-while read IP; do
-    IPS="$IPS\n$IP"
-    COUNTER=$(($COUNTER+1))
-done
-
-IPS=$(echo "$IPS" | grep -v '^$')
-
-
-# ID[$IDS_PER_NODE*$COUNTER] = Node info hashes
-echo "
-import identifier
-for i in range($IDS_PER_NODE*$COUNTER+1):
-    print(repr(identifier.RandomId()))
-
-" | python > /tmp/infohashes.list
-
-
-# ID(0) = info_hash
-# ID(>0) = Node ID
-echo "
-import identifier
-base_ident = repr(identifier.RandomId())
-for i in range($COUNTER+2):
-    ident = repr(identifier.RandomId())
-    ident = base_ident[:30] + ident[30:]
-    print(ident)
-
-" | python > /tmp/infohashes2.list
-cp /tmp/infohashes2.list /tmp/infohashes3.list
-cp /tmp/infohashes$EXPNUM.list /tmp/infohashes.list
+EXPNUM=${1:-1}
+IDS_PER_NODE=${2:-1}
 
 
 FILES="/tmp/infohashes.list bootstrap_unstable experiment$EXPNUM.sh collect.sh"
 
-
 COUNTER=0
-echo -e "$IPS" | while read IP; do
+while read IP; do
     { echo "$IP" &&
       scp -o stricthostkeychecking=no $FILES root@[$IP]: &&
[…]

### 2014-05-22 utils.sh

@@ -1,0 +1,24 @@
+function gen_ids() {
+    # ID[$IDS_PER_NODE*$COUNTER] = Node info hashes
+    echo "
+import identifier
+for i in range($2*$1+1):
+    print(repr(identifier.RandomId()))
+
+" | python > /tmp/infohashes.list
+}
+
+
+function gen_close_ids() {
+    # ID(0) = info_hash
+    # ID(>0) = Node ID
+    echo "
+import identifier
+base_ident = repr(identifier.RandomId())
+for i in range($1+2):
+    ident = repr(identifier.RandomId())
+    ident = base_ident[:30] + ident[30:]
+    print(ident)
+
+" | python > /tmp/infohashes.list
+}

### 2014-05-22 conductor.sh
conductr

@@ -16,6 +16,7 @@ sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-churn3-ids1-cache100
 
 sleep 300
+killall ssh
 
 gen_close_ids $COUNTER
 python split-nodes.py 3 0 | bash deploy.sh 2
@@ -29,6 +30,7 @@ sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp2-cache100-node39
 
 sleep 300
+killall ssh
 
 gen_close_ids $COUNTER
 python split-nodes.py 3 0 | bash deploy.sh 3
@@ -42,6 +44,7 @@ sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp3-cache100
 
 sleep 300
+killall ssh
 
 gen_ids $COUNTER 2
 python split-nodes.py 3 0 | bash deploy.sh 1 2
@@ -55,6 +58,7 @@ sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-churn3-ids2-cache100
 
 sleep 300
+killall ssh
 
 gen_ids $COUNTER 10
 python split-nodes.py 3 0 | bash deploy.sh 1 10
@@ -68,6 +72,7 @@ sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-churn3-ids10-cache100
 
 sleep 300
+killall ssh
 
 gen_close_ids $COUNTER
 sed -i 's/"39"/"102"/' experiment2.sh
@@ -82,6 +87,7 @@ sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp2-cache100-node102
 
 sleep 300
+killall ssh
 
 gen_close_ids $COUNTER
 python split-nodes.py 3 0 | bash deploy.sh 3
@@ -95,6 +101,7 @@ sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp3-cache100-2
 
 sleep 300
+killall ssh
 
 gen_ids $COUNTER 10
 sed -i 's#100/" #10000000/"#' experiment1.sh
@@ -110,16 +117,19 @@ python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-churn3-
 
 
 ##########################
+sleep 300
+killall ssh
 ##########################
 
+
[…]

### 2014-05-22 conductor.sh
conductr

@@ -27,7 +27,7 @@ python split-nodes.py 3 2 | bash deploy.sh 2
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp2-cache100-node39
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp2-churn3-cache100-node39
 
 sleep 300
 killall ssh
@@ -41,7 +41,7 @@ python split-nodes.py 3 2 | bash deploy.sh 3
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp3-cache100
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp3-churn3-cache100
 
 sleep 300
 killall ssh
@@ -84,7 +84,7 @@ python split-nodes.py 3 2 | bash deploy.sh 2
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp2-cache100-node102
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp2-churn3-cache100-node102
 
 sleep 300
 killall ssh
@@ -98,7 +98,7 @@ python split-nodes.py 3 2 | bash deploy.sh 3
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/churn3-exp3-cache100-2
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp3-churn3-cache100-2
 
 sleep 300
 killall ssh

### 2014-05-23 experiment1.sh
Add results

@@ -82,7 +82,7 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 100/" core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/"core/tracker.py
 # Change routing policy
 sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-23 conductor.sh
conductor

@@ -2,8 +2,43 @@ source utils.sh
 
 COUNTER=$(wc -l nodes.list|awk {'print $1'})
 
+
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 200
+
+sed -i 's#CLEANUP_COUNTER = 100/"#CLEANUP_COUNTER = 10000000/"#' experiment11.sh
+gen_ids $COUNTER 2
+python split-nodes.py | bash deploy.sh 11 2
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp11-ids2-cache10000000
+
+sleep 300
+killall ssh
+
+sed -i 's#CLEANUP_COUNTER = 10000000/"#CLEANUP_COUNTER = 100/"#' experiment1.sh
+gen_ids $COUNTER 2
+python split-nodes.py | bash deploy.sh 1 2
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-ids2-cache100
+
+sleep 300
+killall ssh
+
+gen_ids $COUNTER 1
+sed -i 's#10000000/" #100/" #' experiment1.sh
+python split-nodes.py | bash deploy.sh 1 1
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-ids1-cache100
+
+sleep 300
+killall ssh
+
+
+# ORIGINAL
+sed -i 's/sed -i "s\/if rtt/#sed -i "s\/if rtt/' experiment{1,2,3}.sh
+sed -i 's/sed -i "s\/^MAX_NUM_TIMEOUTS/#sed -i "s\/^MAX_NUM_TIMEOUTS/' experiment{1,2,3}.sh
+
+
 gen_ids $COUNTER 1
 python split-nodes.py 3 0 | bash deploy.sh 1 1
 sleep $((20*60))
@@ -13,7 +48,7 @@ python split-nodes.py 3 2 | bash deploy.sh 1 1
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-churn3-ids1-cache100
[…]

### 2014-05-23 experiment1.sh

@@ -82,7 +82,7 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/"core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/"  core/tracker.py
 # Change routing policy
 sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-23 experiment2.sh

@@ -10,7 +10,7 @@ IDS_PER_NODE=$3
 
 SELECTED="False"
 # 102 39
-if [[ "$NODE_NUMBER" == "39" ]]; then
+if [[ "$NODE_NUMBER" == "102" ]]; then
     SELECTED="True"
 fi
 python --version || { apt-get update && apt-get install -y --force-yes git python traceroute ; }

### 2014-05-23 graphs.py

@@ -7,8 +7,18 @@ from pylab import plot,show
 
 
 FILES = '*'
-if len(sys.argv) == 2:
+LONELY = None
+
+if len(sys.argv) > 2:
     FILES = sys.argv[1]
+
+if len(sys.argv) == 3:
+    LONELY = int(sys.argv[2]) + 1
+    with open('nodes.list', 'r') as nodes:
+        for num, line in enumerate(nodes, 1):
+            if num == LONELY:
+                LONELY = "0000000000f9_%s" % line.split(':')[3]
+                break
 
 
 for result in glob.glob('results/' + FILES):
@@ -32,13 +42,14 @@ for result in glob.glob('results/' + FILES):
             else:
                 continue
             
-            nodes.setdefault(node, [])
-            time = int(time.split('.')[0])
-            nodes[node].append((time, hops, latencies))
+            if not LONELY or LONELY == node:
+                nodes.setdefault(node, [])
+                time = int(time.split('.')[0])
+                nodes[node].append((time, hops, latencies))
             
-            key = int(str(time)[:-2] + '00')
-            times.setdefault(key, [])
-            times[key].append((time, hops, latencies))
+                key = int(str(time)[:-2] + '00')
+                times.setdefault(key, [])
+                times[key].append((time, hops, latencies))
         
         plt.figure(1)
         plt.title(result)

### 2014-05-23 experiment11.sh
Added experiment11

@@ -1,0 +1,105 @@
+#!/bin/bash
+
+# Install and launch the experiment
+
+set -e
+
+BOOTSTRAP_ADDR=$1
+NODE_NUMBER=$2
+IDS_PER_NODE=$3
+
+python --version || { apt-get update && apt-get install -y --force-yes git python traceroute ; }
+
+rm -f /root/routing.table
+rm -f /tmp/got_peers.log
+rm -f /tmp/client.log
+rm -rf /root/.pymdht
+mkdir -p /root/.pymdht
+
+if [[ ! -d /root/pymdht ]]; then
+    echo "Cloning PYMDHT ..."
+    git clone https://github.com/rauljim/pymdht.git
+    cd pymdht/
+else
+    cd pymdht/
+    git reset --hard
+fi
+
+echo "Installing client ..."
+echo "
+import time
+import os
+import random
+import socket
+import struct
+
+from core import pymdht, node, identifier
+import plugins.routing_nice_rtt as r_mod
+import plugins.lookup_a4 as l_mod
+import core.exp_plugin_template as e_mod
+
+my_id = identifier.RandomId()
+my_node_info = node.Node(('0.0.0.0', 17000), my_id)
+pymdht_node = pymdht.Pymdht(my_node_info, '/root/.pymdht', r_mod, l_mod, e_mod, None, 1)
+
+def random_peer():
+    ip = socket.inet_ntoa(struct.pack('>I', random.randint(1, 0xffffffff)))
+    return (ip, 17000)
+
+def _got_peers(l_id, peers, node_):
+    with open('/tmp/got_peers.log', 'a') as log:
+        log.write(' '.join((str(peers), str(node_))))
+
+counter = 0
+wait = random.randrange(60, 300)
+while True:
+    # Log routing table entries
+    with open('/root/routing.table', 'a') as log:
+        log.write(' '.join((pid, timestamp, addrs, rtts)) + '\n')
+    time.sleep(2)
+    counter += 1
+    if counter > wait:
+        counter = 0
+        wait = random.randrange(60, 300)
+        # Announce node IDs assigned to this NODE_NUMBER
+        with open('/root/infohashes.list', 'r') as info_file:
+            ini = $NODE_NUMBER*$IDS_PER_NODE
+            end = ($NODE_NUMBER+1)*$IDS_PER_NODE
+            for info_hash in info_file.readlines()[ini:end]:
[…]

### 2014-05-23 conductor.sh
Added experiment11

@@ -2,9 +2,12 @@ source utils.sh
 
 COUNTER=$(wc -l nodes.list|awk {'print $1'})
 
+python split-nodes.py | bash execute.sh "rm routing.hops"
+sleep 100
 
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 200
+sleep 180
+killall ssh
 
 sed -i 's#CLEANUP_COUNTER = 100/"#CLEANUP_COUNTER = 10000000/"#' experiment11.sh
 gen_ids $COUNTER 2
@@ -12,7 +15,7 @@ python split-nodes.py | bash deploy.sh 11 2
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp11-ids2-cache10000000
 
-sleep 300
+sleep 180
 killall ssh
 
 sed -i 's#CLEANUP_COUNTER = 10000000/"#CLEANUP_COUNTER = 100/"#' experiment1.sh
@@ -21,7 +24,7 @@ python split-nodes.py | bash deploy.sh 1 2
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-ids2-cache100
 
-sleep 300
+sleep 180
 killall ssh
 
 gen_ids $COUNTER 1
@@ -30,7 +33,7 @@ python split-nodes.py | bash deploy.sh 1 1
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1-ids1-cache100
 
-sleep 300
+sleep 180
 killall ssh
 
 
@@ -50,7 +53,7 @@ python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment
 sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp1.2-churn3-ids1-cache100-original
 
-sleep 300
+sleep 180
 killall ssh
 
 gen_close_ids $COUNTER
@@ -64,7 +67,7 @@ python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment
 sleep 60
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp2.2-churn3-cache100-node39-original
 
-sleep 300
+sleep 180
 killall ssh
 
 gen_close_ids $COUNTER
[…]

### 2014-05-23 conductor.sh
cond

@@ -2,12 +2,12 @@ source utils.sh
 
 COUNTER=$(wc -l nodes.list|awk {'print $1'})
 
-python split-nodes.py | bash execute.sh "rm routing.hops"
-sleep 100
+#python split-nodes.py | bash execute.sh "rm routing.hops"
+#sleep 100
 
-python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
-sleep 180
-killall ssh
+#python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+#sleep 180
+#killall ssh
 
 sed -i 's#CLEANUP_COUNTER = 100/"#CLEANUP_COUNTER = 10000000/"#' experiment11.sh
 gen_ids $COUNTER 2

### 2014-05-23 deploy.sh
conductr

@@ -25,7 +25,7 @@ COUNTER=0
 while read IP; do
     { echo "$IP" &&
       scp -o stricthostkeychecking=no $FILES root@[$IP]: &&
-      ssh root@$IP 'pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh' ;
+      ssh root@$IP 'pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh; pkill -f experiment11.sh' ;
       CMD="nohup bash experiment$EXPNUM.sh $BOOTSTRAP $COUNTER $IDS_PER_NODE" &&
       echo "$CMD" ;
       ssh root@$IP "$CMD" ;

### 2014-05-23 experiment11.sh
Added experiment11

@@ -88,7 +88,7 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/"core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/" core/tracker.py
 # Change routing policy
 sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-23 conductor.sh
Added results

@@ -15,7 +15,7 @@ python split-nodes.py | bash deploy.sh 11 2
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp11-ids2-cache10000000
 
-sleep 180
+sleep 300
 killall ssh
 
 sed -i 's#CLEANUP_COUNTER = 10000000/"#CLEANUP_COUNTER = 100/"#' experiment1.sh

### 2014-05-23 deploy.sh

@@ -25,7 +25,7 @@ COUNTER=0
 while read IP; do
     { echo "$IP" &&
       scp -o stricthostkeychecking=no $FILES root@[$IP]: &&
-      ssh root@$IP 'pkill -f client.py; pkill -f experiment1.sh; pkill -f experiment2.sh; pkill -f experiment3.sh; pkill -f experiment11.sh' ;
+      ssh root@$IP 'pkill -f client.py; pkill -f bash; pkill -f sleep;';
       CMD="nohup bash experiment$EXPNUM.sh $BOOTSTRAP $COUNTER $IDS_PER_NODE" &&
       echo "$CMD" ;
       ssh root@$IP "$CMD" ;

### 2014-05-23 experiment1.sh

@@ -82,10 +82,10 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Increase cache size
-sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 10000000/"  core/tracker.py
+sed -i "s/^CLEANUP_COUNTER = 100/CLEANUP_COUNTER = 100/"  core/tracker.py
 # Change routing policy
-sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
-sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
+#sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
+#sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
 
 
 echo "$BOOTSTRAP_ADDR 17000" > core/bootstrap_stable

### 2014-05-23 experiment2.sh

@@ -93,8 +93,8 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Change routing policy
-sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
-sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
+#sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
+#sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
 
 
 echo "$BOOTSTRAP_ADDR 17000" > core/bootstrap_stable

### 2014-05-23 experiment3.sh

@@ -77,8 +77,8 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Change routing policy
-sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
-sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
+#sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
+#sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
 
 
 echo "$BOOTSTRAP_ADDR 17000" > core/bootstrap_stable

### 2014-05-24 conductor.sh
added traceroute

@@ -9,6 +9,88 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 #sleep 180
 #killall ssh
 
+
+get_two_bucked_ids $COUNTER
+python split-nodes.py | bash deploy.sh 4
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100
+
+
+sleep 180
+killall ssh
+
+get_two_bucked_ids $COUNTER
+python split-nodes.py 3 0 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py 3 1 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py 3 2 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f bash; pkill -f experiment4.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 60
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-churn3-cache100
+
+
+sleep 180
+killall ssh
+
+# ORIGINAL
+sed -i 's/sed -i "s\/if rtt/#sed -i "s\/if rtt/' experiment4.sh
+sed -i 's/sed -i "s\/^MAX_NUM_TIMEOUTS/#sed -i "s\/^MAX_NUM_TIMEOUTS/' experiment4.sh
+
+get_two_bucked_ids $COUNTER
+python split-nodes.py | bash deploy.sh 4
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-original
+
+
+sleep 180
+killall ssh
+
+get_two_bucked_ids $COUNTER
+python split-nodes.py 3 0 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py 3 1 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py 3 2 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f bash; pkill -f experiment4.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 60
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-churn3-cache100-original
+
+sleep 180
+killall ssh
+
+gen_close_ids $COUNTER
[…]

### 2014-05-24 experiment4.sh

@@ -1,0 +1,92 @@
+#!/bin/bash
+
+# Install and launch the experiment
+
+set -e
+
+BOOTSTRAP_ADDR=$1
+NODE_NUMBER=$2
+IDS_PER_NODE=$3
+
+python --version || { apt-get update && apt-get install -y --force-yes git python traceroute ; }
+
+rm -f /root/routing.table
+rm -f /tmp/got_peers.log
+rm -f /tmp/client.log
+rm -f /root/.pymdht/*
+mkdir -p /root/.pymdht
+
+
+if [[ ! -d /root/pymdht ]]; then
+    echo "Cloning PYMDHT ..."
+    git clone https://github.com/rauljim/pymdht.git
+    cd pymdht/
+else
+    cd pymdht/
+    git reset --hard
+fi
+
+echo "Installing client ..."
+echo "
+import time
+import os
+import random
+import socket
+import struct
+from random import randrange
+
+from core import pymdht, node, identifier
+import plugins.routing_nice_rtt as r_mod
+import plugins.lookup_a4 as l_mod
+import core.exp_plugin_template as e_mod
+
+ident = open('/root/infohashes.list', 'r').readlines()[$NODE_NUMBER+2].strip()
+my_id = identifier.Id(ident)
+my_node_info = node.Node(('0.0.0.0', 17000), my_id)
+pymdht_node = pymdht.Pymdht(my_node_info, '/root/.pymdht', r_mod, l_mod, e_mod, None, 1)
+
+def random_peer():
+    ip = socket.inet_ntoa(struct.pack('>I', random.randint(1, 0xffffffff)))
+    return (ip, 17000)
+
+# Announce node IDs assigned to this NODE_NUMBER
+group = ($NODE_NUMBER+1) % 2
+info_hash = identifier.Id(open('/root/infohashes.list', 'r').readlines()[group].strip())
+
+def _got_peers(l_id, peers, node_):
+    with open('/tmp/got_peers.log', 'a') as log:
+        log.write(' '.join((str(peers), str(node_))))
+
+while True:
+    # Get routing table entries
+    rnodes = pymdht_node.controller._routing_m.get_main_rnodes()
+    addrs = ','.join([ rnode.addr[0] for rnode in rnodes])
+    rtts = ','.join([ '%.2f' % (rnode.rtt*1000) for rnode in rnodes ])
+    pid = str(os.getpid())
[…]

### 2014-05-24 graphs.py

@@ -9,7 +9,7 @@ from pylab import plot,show
 FILES = '*'
 LONELY = None
 
-if len(sys.argv) > 2:
+if len(sys.argv) > 1:
     FILES = sys.argv[1]
 
 if len(sys.argv) == 3:

### 2014-05-24 traceroute.sh

@@ -1,0 +1,10 @@
+#cat nodes.list | while read IP; do scp -o stricthostkeychecking=no traceroute.sh root@[$IP]: &; done
+#cat nodes.list | bash execute.sh "bash traceroute.sh" > hops
+
+
+IPS="10.139.40.123 "$(cat bootstrap_unstable|awk {'print $1'})
+
+for IP in $(echo -n "$IPS"); do
+    ping -c 1 $IP -w 7 &> /dev/null &&
+    traceroute -w 1 -n $IP | tail -n1 | awk {'print $1'} 2> /dev/null
+done

### 2014-05-24 utils.sh

@@ -22,3 +22,19 @@ for i in range($1+2):
 
 " | python > /tmp/infohashes.list
 }
+
+
+function get_two_bucked_ids() {
+    TOTAL=$(($1+4))
+    gen_close_ids $TOTAL
+    ONE=$(cat /tmp/infohashes.list)
+    gen_close_ids $TOTAL
+    TWO=$(cat /tmp/infohashes.list)
+    for i in $(seq $TOTAL); do
+        if [[ $(($i%2)) -eq 0 ]]; then
+            echo -e "$ONE" | sed -n -e ${i}p
+        else
+            echo -e "$TWO" | sed -n -e ${i}p
+        fi
+    done
+}

### 2014-05-24 traceroute.sh
traceroute

@@ -1,10 +1,13 @@
-#cat nodes.list | while read IP; do scp -o stricthostkeychecking=no traceroute.sh root@[$IP]: &; done
-#cat nodes.list | bash execute.sh "bash traceroute.sh" > hops
+#cat nodes.list | while read IP; do scp -o stricthostkeychecking=no traceroute.sh root@[$IP]: & done
+#cat nodes.list | bash execute.sh "bash traceroute.sh" > results/hops
 
 
 IPS="10.139.40.123 "$(cat bootstrap_unstable|awk {'print $1'})
+HOPS=""
 
 for IP in $(echo -n "$IPS"); do
-    ping -c 1 $IP -w 7 &> /dev/null &&
-    traceroute -w 1 -n $IP | tail -n1 | awk {'print $1'} 2> /dev/null
+    ping -c 1 $IP -w 3 &> /dev/null &&
+    HOPS="$HOPS $(traceroute -w 1 -n $IP | tail -n1 | awk {'print $1'} 2> /dev/null)"
 done
+
+echo "$(hostname) $(echo $HOPS | tr ' ' ',')"

### 2014-05-24 conductor.sh
m

@@ -10,7 +10,10 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 #killall ssh
 
 
+sed -i '/DEFAULT_NUM_NODES = 1\/" /DEFAULT_NUM_NODES = 2/" /' experiment4.sh
+
 get_two_bucked_ids $COUNTER
+exit
 python split-nodes.py | bash deploy.sh 4
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100

### 2014-05-24 experiment4.sh

@@ -61,12 +61,17 @@ while True:
     # Get routing table entries
     rnodes = pymdht_node.controller._routing_m.get_main_rnodes()
     addrs = ','.join([ rnode.addr[0] for rnode in rnodes])
-    rtts = ','.join([ '%.2f' % (rnode.rtt*1000) for rnode in rnodes ])
+    rtts = []
+    for rnode in rnodes:
+        self_id = repr(my_id).upper()
+        rnode_id = repr(rnode.id).upper()
+        if not rnode_id.startswith(self_id[:6]):
+            rtts.append('%.2f' % (rnode.rtt*1000))
     pid = str(os.getpid())
     timestamp = str(time.time())
     # Log routing table entries
     with open('/root/routing.table', 'a') as log:
-        log.write(' '.join((pid, timestamp, addrs, rtts)) + '\n')
+        log.write(' '.join((pid, timestamp, addrs, ','.join(rtts))) + '\n')
     pymdht_node.get_peers(ident, info_hash, _got_peers)
     pymdht_node.controller._tracker.put(info_hash, random_peer())
     time.sleep(50)

### 2014-05-24 conductor.sh
cond

@@ -10,7 +10,7 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 #killall ssh
 
 
-get_two_bucked_ids $COUNTER
+mv /tmp/infohashes.list1 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100
@@ -19,7 +19,7 @@ python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache10
 sleep 180
 killall ssh
 
-get_two_bucked_ids $COUNTER
+mv /tmp/infohashes.list2 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh 4
@@ -38,7 +38,7 @@ killall ssh
 sed -i 's/sed -i "s\/if rtt/#sed -i "s\/if rtt/' experiment4.sh
 sed -i 's/sed -i "s\/^MAX_NUM_TIMEOUTS/#sed -i "s\/^MAX_NUM_TIMEOUTS/' experiment4.sh
 
-get_two_bucked_ids $COUNTER
+mv /tmp/infohashes.list3 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-original
@@ -47,7 +47,7 @@ python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache10
 sleep 180
 killall ssh
 
-get_two_bucked_ids $COUNTER
+mv /tmp/infohashes.list4 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh 4

### 2014-05-24 experiment4.sh

@@ -78,8 +78,8 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Change routing policy
-sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
-sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
+#sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
+#sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
 
 
 echo "$BOOTSTRAP_ADDR 17000" > core/bootstrap_stable

### 2014-05-24 utils.sh

@@ -36,5 +36,5 @@ function get_two_bucked_ids() {
         else
             echo -e "$TWO" | sed -n -e ${i}p
         fi
-    done
+    done > /tmp/infohashes.list
 }

### 2014-05-24 conductor.sh
m

@@ -13,11 +13,24 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 mv /tmp/infohashes.list1 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
 sleep $((62*60))
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-nodes1
 
 
 sleep 180
 killall ssh
+
+
+sed -i 's/DEFAULT_NUM_NODES = 1\/" /DEFAULT_NUM_NODES = 2\/" /' experiment4.sh
+
+python split-nodes.py | bash deploy.sh 4
+sleep $((62*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-nodes2
+
+sleep 180
+killall ssh
+
+
+sed -i 's/DEFAULT_NUM_NODES = 2\/" /DEFAULT_NUM_NODES = 1\/" /' experiment4.sh
 
 mv /tmp/infohashes.list2 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
@@ -28,20 +41,38 @@ python split-nodes.py 3 2 | bash deploy.sh 4
 sleep $((20*60))
 python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f bash; pkill -f experiment4.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
 sleep 60
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-churn3-cache100
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-churn3-cache100-nodes1
 
 
 sleep 180
 killall ssh
 
+
+
+sed -i 's/DEFAULT_NUM_NODES = 1\/" /DEFAULT_NUM_NODES = 2\/" /' experiment4.sh
+
+python split-nodes.py 3 0 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py 3 1 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py 3 2 | bash deploy.sh 4
+sleep $((20*60))
+python split-nodes.py | bash execute.sh "pkill -f client.py; pkill -f bash; pkill -f experiment4.sh; pkill -f experiment2.sh; pkill -f experiment3.sh"
+sleep 60
[…]

### 2014-05-24 conductor.sh
m

@@ -12,39 +12,66 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 
 mv /tmp/infohashes.list1 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
-sleep $((62*60))
+sleep $((12*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-nodes1
 
+sleep 100
+python split-nodes.py | bash execute.sh "pkill -f client.py;"
+python split-nodes.py | bash execute.sh "pkill -f bash;"
+python split-nodes.py | bash execute.sh "pkill -f sleep;"
+sleep 80
 
-sleep 180
 killall ssh
 
 
 sed -i 's/DEFAULT_NUM_NODES = 1\/" /DEFAULT_NUM_NODES = 2\/" /' experiment4.sh
 
 python split-nodes.py | bash deploy.sh 4
-sleep $((62*60))
+sleep $((12*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-nodes2
 
-sleep 180
+sleep 100
+python split-nodes.py | bash execute.sh "pkill -f client.py;"
+python split-nodes.py | bash execute.sh "pkill -f bash;"
+python split-nodes.py | bash execute.sh "pkill -f sleep;"
+sleep 80
+
 killall ssh
 
 
-sed -i 's/DEFAULT_NUM_NODES = 2\/" /DEFAULT_NUM_NODES = 1\/" /' experiment4.sh
+sed -i 's/DEFAULT_NUM_NODES = 2\/" /DEFAULT_NUM_NODES = 3\/" /' experiment4.sh
+
+python split-nodes.py | bash deploy.sh 4
+sleep $((12*60))
+python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-nodes3
+
+sleep 100
+python split-nodes.py | bash execute.sh "pkill -f client.py;"
+python split-nodes.py | bash execute.sh "pkill -f bash;"
+python split-nodes.py | bash execute.sh "pkill -f sleep;"
+sleep 80
+
+killall ssh
+
+sed -i 's/DEFAULT_NUM_NODES = 3\/" /DEFAULT_NUM_NODES = 1\/" /' experiment4.sh
 
 mv /tmp/infohashes.list2 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
[…]

### 2014-05-24 conductor.sh
d

@@ -9,8 +9,10 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 #sleep 180
 #killall ssh
 
+#get_two_bucked_ids $COUNTER
+#exit
 
-mv /tmp/infohashes.list1 /tmp/infohashes.list
+cp /tmp/infohashes.list1 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-nodes1
@@ -32,7 +34,7 @@ killall ssh
 
 sed -i 's/DEFAULT_NUM_NODES = 2\/" /DEFAULT_NUM_NODES = 1\/" /' experiment4.sh
 
-mv /tmp/infohashes.list2 /tmp/infohashes.list
+cp /tmp/infohashes.list2 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh 4
@@ -69,7 +71,7 @@ sed -i 's/sed -i "s\/if rtt/#sed -i "s\/if rtt/' experiment4.sh
 sed -i 's/sed -i "s\/^MAX_NUM_TIMEOUTS/#sed -i "s\/^MAX_NUM_TIMEOUTS/' experiment4.sh
 
 
-mv /tmp/infohashes.list3 /tmp/infohashes.list
+cp /tmp/infohashes.list3 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
 sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-original-nodes2
@@ -78,7 +80,7 @@ python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache10
 sleep 180
 killall ssh
 
-mv /tmp/infohashes.list4 /tmp/infohashes.list
+cp /tmp/infohashes.list4 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
 sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh 4

### 2014-05-24 conductor.sh
results

@@ -101,18 +101,6 @@ sed -i 's/sed -i "s\/if rtt/#sed -i "s\/if rtt/' experiment4.sh
 sed -i 's/sed -i "s\/^MAX_NUM_TIMEOUTS/#sed -i "s\/^MAX_NUM_TIMEOUTS/' experiment4.sh
 
 
-cp /tmp/infohashes.list3 /tmp/infohashes.list
-python split-nodes.py | bash deploy.sh 4
-sleep $((12*60))
-python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4-cache100-original-nodes2
-sleep 100
-python split-nodes.py | bash execute.sh "pkill -f client.py;"
-python split-nodes.py | bash execute.sh "pkill -f bash;"
-python split-nodes.py | bash execute.sh "pkill -f sleep;"
-
-sleep 80
-killall ssh
-
 gen_close_ids $COUNTER
 python split-nodes.py | bash deploy.sh 3
 sleep $((62*60))

### 2014-05-24 experiment4.sh

@@ -84,8 +84,8 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Change routing policy
-#sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
-#sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
+sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
+sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
 
 
 echo "$BOOTSTRAP_ADDR 17000" > core/bootstrap_stable

### 2014-05-26 conductor.sh
m0

@@ -14,7 +14,7 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 
 cp /tmp/infohashes.list1 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
-sleep $((30*60))
+sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4.3-cache100-nodes1
 
 sleep 100
@@ -24,13 +24,12 @@ python split-nodes.py | bash execute.sh "pkill -f sleep;"
 sleep 80
 
 killall ssh
-exit
 
 sed -i 's/DEFAULT_NUM_NODES = 1\/" /DEFAULT_NUM_NODES = 2\/" /' experiment4.sh
 cp /tmp/infohashes.list2 /tmp/infohashes.list
 
 python split-nodes.py | bash deploy.sh 4
-sleep $((30*60))
+sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4.2-cache100-nodes2
 
 sleep 100
@@ -46,7 +45,7 @@ sed -i 's/DEFAULT_NUM_NODES = 2\/" /DEFAULT_NUM_NODES = 3\/" /' experiment4.sh
 cp /tmp/infohashes.list3 /tmp/infohashes.list
 
 python split-nodes.py | bash deploy.sh 4
-sleep $((12*60))
+sleep $((62*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4.2-cache100-nodes3
 
 sleep 100
@@ -61,11 +60,11 @@ sed -i 's/DEFAULT_NUM_NODES = 3\/" /DEFAULT_NUM_NODES = 1\/" /' experiment4.sh
 
 cp /tmp/infohashes.list4 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
-sleep $((10*60))
+sleep $((20*60))
 python split-nodes.py 3 1 | bash deploy.sh 4
-sleep $((10*60))
+sleep $((20*60))
 python split-nodes.py 3 2 | bash deploy.sh 4
-sleep $((10*60))
+sleep $((20*60))
 sleep 100
 python split-nodes.py | bash execute.sh "pkill -f client.py;"
 python split-nodes.py | bash execute.sh "pkill -f bash;"
@@ -79,16 +78,15 @@ sleep 100
[…]

### 2014-05-26 experiment4.sh

@@ -88,7 +88,7 @@ echo "Patching pymdht..."
 # try to prevent minitwisted to crash ...
 sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnets.remove(utils.get_subnet(addr))\n        except KeyError: pass/" core/bootstrap.py
 # Adapt bucket dimensioning to our DHT small size
-sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 2/" plugins/routing_nice_rtt.py
+sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
 # Change routing policy
 #sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 #sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-26 experiment4.sh
m0

@@ -88,7 +88,7 @@ echo "Patching pymdht..."
 # try to prevent minitwisted to crash ...
 sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnets.remove(utils.get_subnet(addr))\n        except KeyError: pass/" core/bootstrap.py
 # Adapt bucket dimensioning to our DHT small size
-sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 1/" plugins/routing_nice_rtt.py
+sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 2/" plugins/routing_nice_rtt.py
 # Change routing policy
 #sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
 #sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py

### 2014-05-26 conductor.sh
f

@@ -14,7 +14,7 @@ COUNTER=$(wc -l nodes.list|awk {'print $1'})
 
 cp /tmp/infohashes.list1 /tmp/infohashes.list
 python split-nodes.py | bash deploy.sh 4
-sleep $((62*60))
+sleep $((32*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4.3-cache100-nodes1
 
 sleep 100
@@ -29,7 +29,7 @@ sed -i 's/DEFAULT_NUM_NODES = 1\/" /DEFAULT_NUM_NODES = 2\/" /' experiment4.sh
 cp /tmp/infohashes.list2 /tmp/infohashes.list
 
 python split-nodes.py | bash deploy.sh 4
-sleep $((62*60))
+sleep $((32*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4.2-cache100-nodes2
 
 sleep 100
@@ -45,7 +45,7 @@ sed -i 's/DEFAULT_NUM_NODES = 2\/" /DEFAULT_NUM_NODES = 3\/" /' experiment4.sh
 cp /tmp/infohashes.list3 /tmp/infohashes.list
 
 python split-nodes.py | bash deploy.sh 4
-sleep $((62*60))
+sleep $((32*60))
 python split-nodes.py | bash execute.sh "bash collect.sh" > results/exp4.2-cache100-nodes3
 
 sleep 100
@@ -60,11 +60,11 @@ sed -i 's/DEFAULT_NUM_NODES = 3\/" /DEFAULT_NUM_NODES = 1\/" /' experiment4.sh
 
 cp /tmp/infohashes.list4 /tmp/infohashes.list
 python split-nodes.py 3 0 | bash deploy.sh 4
-sleep $((20*60))
+sleep $((10*60))
 python split-nodes.py 3 1 | bash deploy.sh 4
-sleep $((20*60))
+sleep $((10*60))
 python split-nodes.py 3 2 | bash deploy.sh 4
-sleep $((20*60))
+sleep $((10*60))
 sleep 100
 python split-nodes.py | bash execute.sh "pkill -f client.py;"
 python split-nodes.py | bash execute.sh "pkill -f bash;"

### 2014-05-26 experiment4.sh

@@ -90,8 +90,8 @@ sed -i "s/self._all_subnets.remove(utils.get_subnet(addr))/try: self._all_subnet
 # Adapt bucket dimensioning to our DHT small size
 sed -i "s/^DEFAULT_NUM_NODES = 8/DEFAULT_NUM_NODES = 2/" plugins/routing_nice_rtt.py
 # Change routing policy
-#sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
-#sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
+sed -i "s/^MAX_NUM_TIMEOUTS = 2/MAX_NUM_TIMEOUTS = -1/" plugins/routing_nice_rtt.py
+sed -i "s/if rtt < rnode.rtt \* (1 - (rnode_age \/ 7200)):/if rtt < rnode.rtt:/" plugins/routing_nice_rtt.py
 
 
 echo "$BOOTSTRAP_ADDR 17000" > core/bootstrap_stable

### 2014-05-29 paper.tex
Added paper

\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx}
\usepackage{url}
\usepackage{listings}
\usepackage{float}

\graphicspath{ {images/} }

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Evaluation of the locality of the Mainline DHT}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Marc Aymerich}
\IEEEauthorblockA{Universitat Politecnica de Catalunya}
Email: marc.aymerich@est.fib.upc.edu
\and
\IEEEauthorblockN{Unai Perez}
\IEEEauthorblockA{Universitat Politecnica de Catalunya}
Email: unai.perez@est.fib.upc.edu
\and
\IEEEauthorblockN{Be\~nat Txurruka}
\IEEEauthorblockA{Universitat Politecnica de Catalunya}
Email: benat.txurruka@est.fib.upc.edu}

% make the title area
\maketitle

\begin{abstract}
Community Networks (CN) are an emerging bottom-up model where communities of citizens build, operate and own open IP-based networks. In contrast to the traditional Internet, the core of these networks is build using unreliable wireless links and cheap low-end forwarding devices. For this reason, locality-aware applications become particular important in Community Networks.

Distributed Hash Tables (DHT), is a well known and mature decentralized key-value store system. Mainline DHT, the larger DHT deployed world-wide, is commonly used for storing BitTorrent peers, but it works for arbitrary data as well. Even though, Mainline DHT specifications do not provide mechanism that encourage locality, we have done so by choosing a particular \textit{Proximity Neighbour Selection} routing policy that encourages locality by choosing routing nodes with the lower round-trip-time (RTT).

In this paper we provide a preliminary study of the locality characteristics of the Mainline DHT using PYMDHT and one of its routing policies based on RTT measurements.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
DHT, MLDHT, API, P2P, CDNS, CN, RTT, ID, IP, UDP, TTL
\end{IEEEkeywords}

\section{Introduction}

Distributed Hash Table (DHT) is a decentralized system that provides look-up services similar to hash tables; (key, values) pairs are stored in a DHT, and any particular node can efficiently retrieve the associated value\cite{b30}. The decentralized nature and the scalability characteristics of DHT makes it the preferred way for storing shared state on P2P applications (e.g. peer lists). Kademlia and Mainline DHT are the most widely deployed DHTs world wide, creating overlay networks of millions of nodes \cite{b1}.

However, DHT not only serves good for storing peer swarms on P2P applications. DHT overlay networks are used on a large variety of Internet services. Some examples are, CDNS \cite{b2,b3}, application-level multicast, instant messaging, domain name services, web caching or distributed file systems.

On the other hand, DHT technologies are mainly evolving towards the Internet. And even though, emerging networks like Community Networks (CN)\footnote{\url{http://en.wikipedia.org/wiki/Community_network}} are based on the same fundamental technology than Internet, they also have their own discrepancies and peculiarities.

Community Networks raise from the dramatic drop of wireless network equipment cost over the last decade which has enabled end-users to build their own network independently from traditional telecommunications providers. This has a dramatic impact on the network properties. Most of its traffic flows through short-distance, low-throughput, high-latency wireless links, build with cheap low-end hardware.

The topology characteristics of Community Networks are also a bit different from the traditional Internet. On village-like environments, typical CN deployment may involve a single Access Point on the top-roof of the village from which all the clients connect to. On cities, usually the topology is a mesh-like network. Therefore, in both cases the network tends to forms clusters of nodes with a very few hops between each other but interconnected by long-distance inter-village wireless links.

Locality-aware applications become much important in CN because the cost of leaving the neighborhood is particularly expensive since it may involve transiting through several kilometers of unreliable microwave links, with significative packet loss, jitter, high latency and low throughput.

In this paper, we study the locality characteristics of DHT overlay on the context of Community Networks. In the next section background on DHT locality is presented.

%/////////////////////////////////////////////////////////////////////////////
\section{Background}

Network locality (proximity) in Distributed Hash Tables has been extensively studied \cite{b10, b11, b12, b31}. Three basic approaches have been suggested for exploring proximity in DHT protocols:

\subsection{Geographic Layout}

The node IDs are assigned in a manner that ensures that nodes that are close in the network topology are close in the node ID space. Geographic Layout was explored as one technique to improve routing performance in CAN \cite{b4}. In one implementation, nodes measure the RTT between themselves and a set of landmark servers to compute the coordinates of the node in the CAN space.

\subsection{Proximity Routing}

The routing tables are built without taking network proximity into account but the routing algorithm chooses a nearby node at each hop from among the ones in the routing table. Proximity routing was first proposed in CAN \cite{b4}. It involves no changes to routing table construction and maintenance, because routing tables are built without taking network proximity into account.

\subsection{Proximity Neighbour Selection}

Routing table construction takes network proximity into account. Routing table entries are chosen to refer to nodes that are nearby in the network topology, among all live nodes with appropriate node IDs. Proximity neighbour selection is used in Tapestry and Pastry.

\textit{Geographic Layout} techniques are very effective for building overlays with a high degree of physical locality. However, we found that in the context of Community Networks it may not be the best choice. Network splits are common due to both, hardware malfunction (low-end hardware used) and human errors during management operations (intrinsic complexity of operating a highly decentralized network).

Because of network splits, a perfect locality based on \textit{Geographic Layout} may lead to entire portions of the DHT ID space inaccessible. In this sense, Proximity Routing and Proximity Neighbour Selection provides far better reliability since the Node IDs have nothing to do with the geographic location.

Intuitively, \textit{Proximity Routing} may not work as good as \textit{Proximity Neighbour Selection}. Because the routing table is small (compared to the total number of nodes), there are not many candidates to choose from. Also prioritizing underlay locality over overlay locality may actually lead to an increase on the number of hops for DHT look-up operations.

We believe that \textit{Proximity Neighbour Selection} offers the best properties for deployment on CN. ID space is uniformly distributed over the whole network, making it robust, while good enough locality can still be achieved by choosing nearby nodes as routing table entries.

\section{Mainline DHT}

We based our DHT evaluation on Mainline DHT (MLDHT). MLDHT is a Kademlia-based Distributed Hash Table used by BitTorrent clients to find peers via the BitTorrent protocol. MLDHT is the largest DHT network currently deployed in the Internet, measures from 2013 show from 10 million to 25 million users, with a daily churn of at least 10 million [1].

Mainline DHT protocol is actually pretty simple, limited to four control messages:

\begin{enumerate}
\item \texttt{PING}: probe a node's availability. If the node fails to respond for some time, it will be purged out of the routing table
\item \texttt{FIND\_NODE}: given a target ID, this message is used to find the \{k\} closest neighbors of the ID
\item \texttt{GET\_PEERS}: given an infohash, get the initial peer set. Notice that BitTorrent peer locality is also an interesting factor, but its evaluation is not the objective of this work
\item \texttt{ANNOUNCE\_PEER}: a peer announces it belongs to a swarm
\end{enumerate}

Its simplicity and the fact that it is a widely deployed protocol makes its evaluation study somehow easier, since the complexity is low and there are several MLDHT implementations to choose from. We looked at libtorrent and PYMDHT.

libtorrent \cite{b6} was our first consideration, is a well known open source implementation of BitTorrent protocol and it has support for Mainline DHT. However, we quickly found out that its public API provides little information about the DHT routing state, only providing the node ID of each entry, not the IP address nor RTT measurements. This is not surprising since its design is focused on BitTorrent applications, not on DHT routing evaluation. Also libtorrent implements a highly tune and complicated routing algorithm with a lot of corner cases and optimizations making its behaviour less predictable \cite{b1}.

PYMDHT \cite{b8} is a flexible Python implementation of the Mainline DHT protocol, specifically designed for MDHT evaluation. This is the main reason why we choose PYMDHT over libtorrent, even though PYMDHT current state is experimental, the codebase has room for improvement and there is no public documentation available.

Mainline DHT, as described in BitTorrent Enhancement Proposal 5 (BEP5) \cite{b9}, does not consider any means for locality. However, implementers of this DHT are free to choose whatever routing policy they wish to. In the case of PYMDHT a plugging system is in place for easily switching between routing policies. Moreover, the library ships with an implementation of a \textit{Proximity Neighbour Selection} routing policy defined by NICE \cite{b18}, based on RTT measurements, which is very convenient as a foundation for our locality evaluation.

\section{MLDHT Locality Evaluation on \\ Community Lab}

The testbed of choice for our evaluation is Community Lab\footnote{\url{http://community-lab.net/}}, a Community Networks Testbed by the CONFINE project that provides a global facility for experimentation with network technologies and services for Community Networks \cite{b16}.

Our experiments take place on a 140 node slice, the whole set of Community Lab nodes at this time. Unfortunately, the amount of effectively available nodes is severely reduced by several factors.
\begin{itemize}
\item Around 63 nodes are in offline state most of the time
\item 20 nodes do not have Internet connectivity, needed for installing
dependencies
\item 5 nodes report a "Fail allocate" state
\item 3 nodes remian in "Unknown" state
\item From those online, 17 do not have IP connectivity with the rest \footnote{\url{https://github.com/glic3rinu/MLDHT-locality/blob/master/results/hops}}. Some of them because a lack of public IP addresses and others because of inadequate federation between CN
\end{itemize}

This leaves us with a total amount of around 26 usable nodes. Moreover, we have seen PYMDHT instances to randomly crash in several occasions, further decreasing the total number of operative DHT nodes.

Because of the reduced number of available nodes in our testbed, special care is needed in order to design experiments that produce any significant result about the locality properties. Remember that MLDHT is build with Internet scale in mind, with millions of nodes in size. The original Mainline DHT as defined in BEP5 specifies an ID space of 160 bits, which translates to 160 buckets, a lot more than nodes on our testbed.

Some changes on the original PYMDHT implementation had been performed in order to accommodate our tiny DHT.
\begin{itemize}
\item \texttt{DEFAULT\_NUM\_NODES}, 8 by default, controls the number of nodes per bucket and it has been reduced to 1 in order to have a larger set of competing nodes for each bucket
\item \texttt{MAX\_NUM\_TIMEOUTS}, 2 by default, determines how many sequential timeouts are allowed for a routing entry before being replaced. We set its value to -1 in order to have a faster convergence of routing table entries locality
\item  The original NICE RTT routing policy applies a decreasing factor to the candidate RTT

\begin{lstlisting}[language=python]
rnode.rtt * (1 - (rnode_age / 7200))
\end{lstlisting}

For instance, when routing node has been in the bucket for 30 minutes, a candidate's RTT must be at most 25\% of the routing node's RTT (ie. two times faster). After two hours, a routing node cannot be replaced by this method. In order to give RTT a higher weight, this factor has been eliminated from the conditions needed for new routing entries.
\item  Reducing the ID space, and thus reducing the number of buckets, has been proposed but finally not implemented because multiple parts of PYMDHT's codebase makes assumptions about the ID space size. However, we use crafted node IDs and infohashes (not randomly generated), in order to artificially reduce the effective amount of buckets (e.g. generate some IDs that belong to a particular bucket).
\end{itemize}

Considering that, round-trip time (RTT) is the only locality-related metric used by our routing policy, one may argue that RTT may not be reliable enough in CN because of the high jitter of most wireless links (latency variation). In that effect, distance measured by UDP packets with a crafted time-to-live (TTL), a.k.a. traceroute, may also be an interesting metric to consider for inclusion on the DHT routing algorithm. However, this metric is not available at this time.

By executing traceroute on each node\footnote{\url{https://github.com/glic3rinu/MLDHT-locality/blob/master/traceroute.sh}} we have calculated the average number of hops on the whole network. Which in our case is 7.5 (with an standard deviation of 5.2). This number can be used as a reference point in order to evaluate how good or bad is the locality in our nodes routing tables.

Additionally, we have to take into account that some nodes are between 11 and 18 hops from the nearest node. We have considered to threat those nodes as outliers, but we finally discarded this idea since doing so will reduce even further the amount of nodes on our DHT. And because of the topology characteristics of Community Lab, almost all remaining nodes will be sitting on a laboratory, one next to the other.

In the next sections the results of locality evaluation of the DHT routing table entries are presented. Notice that, because of the limited size of our DHT, the workload of each experiment has been crafted in order to artificially promote locality rather than focus on more realistic workloads. All the experiments and results are publicly available at Github\footnote{\url{https://github.com/glic3rinu/MLDHT-locality}}.

\subsection{High Load Workload}

Each DHT node announces N infohashes and periodically performs a \texttt{GET\_PEERS} of all the other nodes announced infohashes, after randomly waiting between 60 and 300 seconds. The total number of \texttt{GET\_PEERS} queries performed on the DHT every minute will be greater than $\frac{1}{4} (NUM\_NODES-1) \cdot N$, since an initial query may involve several recursive queries before completion.

\begin{figure}
    \includegraphics[width=\columnwidth]{exp1,1-ids1-cache0.png}
    \caption{\textit{High Load Workload} results. Sub-figure 1: average number of hops on the routing table. Sub-figure 2: average latency per node on the the routing table. Sub-figure 3: green triangles is the average of the average number of hops, blue squares is the average of the average latency.}
    \label{fig:exp1,1-ids1-cache0}
\end{figure}

Figure \ref{fig:exp1,1-ids1-cache0} shows an steady average of 6 hops, a value very close to the network mean 7.5. This is because nodes perform queries to random buckets, and because we have an average of less than one node per bucket $26/160$, there is no chance for the routing policy to perform any kind of selection based on RTT measurements.

A second round of this workload has been executed but now with caching enabled. After a very few rounds \texttt{GET\_PEERS} results are cached over several nodes. Thus, giving more chance to lower latency nodes to be selected as routing nodes.

\begin{figure}
    \includegraphics[width=\columnwidth]{exp1-ids1-cache100.png}
    \caption{\textit{High Load Workload with caching} results. Sub-figure 1: average number of hops on the routing table. Sub-figure 2: average latency per node on the the routing table. Sub-figure 3: green triangles is the average of the average number of hops, blue squares is the average of the average latency.}
    \label{fig:exp1-ids1-cache100}
\end{figure}

In figure \ref{fig:exp1-ids1-cache100} we see how caching seems to makes convergence to a better locality value, but repetitions of this same experiments shown mixed results. At this point we are not able to conclude that caching leads to better locality, at least in our 26 node DHT. However, caching seems to affect the patter on the routing table hops and latencies, compared with fig. \ref{fig:exp1,1-ids1-cache0}.

In order to see how churn affects locality we have divided the experiment in 3 phases. In each phase 1/3 of our nodes are added to the DHT. The idea behind this is to gradually increase the number of nearby nodes and see how the routing algorithm adapts to it.

\begin{figure}
    \includegraphics[width=\columnwidth]{churn-1.png}
    \caption{\textit{High Load Workload with churn} results. Sub-figure 1: average number of hops on the routing table. Sub-figure 2: average latency per node on the the routing table. Sub-figure 3: green triangles is the average of the average number of hops, blue squares is the average of the average latency.}
    \label{fig:churn-1}
\end{figure}

In Figure \ref{fig:churn-1} we can see the gradual selection of nearer nodes as they become available during the 3 phases of the experiment.

\subsection{Close IDs Workload}

All node's 120 most significant bits are the same, also an infohash with the same characteristics is inserted in the DHT and all the nodes perform periodic \texttt{GET\_PEERS} requests of this infohash.

This workload is designed to characterize the locality of nearby nodes in terms of the overlay network. Since our DHT size is very small, we decided to force all the nodes to be compacted on the same portion of the ID space in order to determine how the routing policy performs with some logical nearby nodes.

\begin{figure}
    \includegraphics[width=\columnwidth]{exp3,2-cache100-2-original.png}
    \caption{\textit{Close IDs Workload} results. Sub-figure 1: average number of hops on the routing table. Sub-figure 2: average latency per node on the the routing table. Sub-figure 3: green triangles is the average of the average number of hops, blue squares is the average of the average latency.}
    \label{fig:exp3,2-cache100-2-original}
\end{figure}

Because of the bucket distribution, based on logarithmic distance, much more buckets are reserved for nearby IDs. Figure \ref{fig:exp3,2-cache100-2-original} shows an steady average of 4 hops, better than the average number of hops on the whole network (7.5). Our guess is that the routing algorithm stabilizes very quickly during bootstrap and then the routing table remains intact because of the lack of churn. A sign of this early stabilization is the flat patter on the number of hops and latencies plots.

\begin{figure}
    \includegraphics[width=\columnwidth]{exp3-churn3-cache100-2.png}
    \caption{\textit{Close IDs Workload with churn} results. Sub-figure 1: average number of hops on the routing table. Sub-figure 2: average latency per node on the the routing table. Sub-figure 3: green triangles is the average of the average number of hops, blue squares is the average of the average latency.}
    \label{fig:exp3-churn3-cache100-2}
\end{figure}

In Figure \ref{fig:exp3-churn3-cache100-2} we see that churn actually harms locality. The reason might be that 26 nodes are not enough to fill the amount of buckets assigned for closer IDs (logarithmic distribution), and thus, close ID nodes are preferred over the physically near ones.

\subsection{Lonely Node Workload}

This experiment also uses crafted node IDs to force all node's ID being in the same bucket, from the lonely node point of view. We want to create a lot of bucket competition on the lonely node routing table and validate that the physically nearest node is always chosen.

Interestingly enough, Community Lab topology includes the type of node clustering commonly seen in Community Network villages and described on the introductory chapter. In the case of Community Lab those are the nodes at UPC-Lab, where only one forwarding device sits between the nodes \cite{b19}.

The lonely node is selected from this cluster since it will have plenty of nearby candidates to choose from. Figure \ref{fig:exp2,2-cache100-node39-original} illustrates the results of this experiment.

\begin{figure}
    \includegraphics[width=\columnwidth]{exp2,2-cache100-node39-original.png}
    \caption{\textit{Lonely Node Workload} results. Sub-figure 1: average number of hops on the routing table. Sub-figure 2: average latency per node on the the routing table. Sub-figure 3: green triangles is the average of the average number of hops, blue squares is the average of the average latency.}
    \label{fig:exp2,2-cache100-node39-original}
\end{figure}

\subsection{Two Buckets Workload}

Perhaps this experiment is the most interesting of all. In order to effectively reduce the number of buckets on the overlay we have generated node IDs that belong to two different buckets. And then each group of nodes perform \texttt{GET\_PEERS} queries to the other group's infohash. Therefore, we have plenty of routing nodes competing for the same position on the routing tables. We call this bucket, the \textit{competing bucket}.

\begin{figure}
    \includegraphics[width=\columnwidth]{exp4,2-cache100-nodes1.png}
    \caption{\textit{Two Buckets Workload} results. Sub-figure 1: average number of hops per node on the \textit{competing bucket}. Sub-figure 2: average latency per node on the \textit{competing bucket}. Sub-figure 3: green triangles is the average of the average number of hops, blue squares is the average of the average latency.}
    \label{fig:exp4,2-cache100-nodes1}
\end{figure}

Figure \ref{fig:exp4,2-cache100-nodes1} shows the results, in this case we only measure the \textit{competing bucket} and not the buckets that belong to the node's own group. The results are not as good as expected, 5 hops on average, below the average hops on the network (7.5). Perhaps the fact that some nodes have the nearest neighbor at 11-18 hops makes the average number of hops a bad locality evaluator. Maybe a more powerful statistical analysis of the results could provide a partial, or total, explanation to this bad score. Additionally, Figure \ref{fig:exp4,2-cache100-nodes1} shows that MLDHT needs some minutes to stabilize the routing table.

\section{Future Work}

The main limitation of our evaluation is the reduced number of nodes in our testbed. Further analysis should be performed in order to better understand the locality characteristics of Mainline DHT, specially under realistic workloads.

Solely using the average number of hops may not be a good enough locality evaluator. A better one could be the average number of hops of the routing entries over the average number of hops to other nodes, ($\frac{avg(routing\_hops)}{avg(total\_hops}$), or even better, the potential optimal value over the current value. In short, making the values dependent of each node will give a better fit.

Measurements of the number of underlay hops of the \texttt{ANNOUNCE\_PEER} and \texttt{GET\_PEERS} queries are missing in our evaluation, but are key measurements to better understand locality in a DHT.

An interesting extension of our work could be estimate how locality-aware routing policy affects response time and other performance characteristics of Mainline DHT.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

\section{Conclusion}
In this paper we have shown that locality in Mainline DHT can be achieved with a very simple routing policy bases on \textit{Proximity Neighbour Selection} with RTT measurements. We also show that Mainline DHT, as defined in BEP5, is designed specifically for Internet scale deployments, changes on the DHT dimensions are required in order to properly accommodate smaller deployments, for instance, thus on Community Networks.

We have also seen the limitations of having an small number of nodes. Leading to the need of crafting node IDs and infohashes and to design experiments very carefully in order to have any significant result.

We consider this study very preliminary, further evaluations, with more powerful statistical analysis and more nodes, are needed in order to better quantify the locality properties and their performance implications.

% use section* for acknowledgement
\section*{Acknowledgment}

%The authors would like to thank...

We would like to thank Raul Jimenez from Royal Institute of Technology (KTH) and
Leandro Navarro from Universitat Politecnica de Catalunya (UPC), for their advice, help and interest during the realization of this project.

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\bibitem{b1}
Wang, Liang, and Jussi Kangasharju. "Measuring large-scale distributed systems: case of BitTorrent Mainline DHT." Peer-to-Peer Computing (P2P), 2013 IEEE Thirteenth International Conference on. IEEE, 2013.

\bibitem{b2}
Akamai, \url{www.akamai.com}

\bibitem{b3}
Digital island, \url{http://www.digitalisland.co.nz/}

\bibitem{b4}
Exploring Network Proximity

\bibitem{b5}
LDHT

\bibitem{b6}
Rasterbar Software, \emph{libtorrent}, \url{http://www.rasterbar.com/products/libtorrent/}, 2005

\bibitem{b8}
Raul Jimenez, \emph{pymdht}, \url{https://github.com/rauljim/pymdht}, 2009-2012

\bibitem{b9}
BitTorrent Enhancement Proposals, \url{http://www.bittorrent.org/beps/bep_0005.html}

\bibitem{b10}
Wu, Weiyu, et al. "LDHT: locality-aware distributed hash tables." Information Networking, 2008. ICOIN 2008. International Conference on. IEEE, 2008.

\bibitem{b11}
Ferreira, Ronaldo A., Suresh Jagannathan, and Ananth Grama. "Locality in structured peer-to-peer networks." Journal of Parallel and Distributed Computing 66.2 (2006): 257-273.

\bibitem{b12}
Zhou, Shuheng, Gregory R. Ganger, and Peter Alfons Steenkiste. "Location-based node ids: Enabling explicit locality in dhts." (2003).

\bibitem{b16}
CONFINE Project, \url{http://confine-project.eu/}

\bibitem{b18}
UMD, \url{http://www.cs.umd.edu/projects/nice/}

\bibitem{b19}
Community-Lab, \url{http://monitor.confine-project.eu:8000/networktrace/}

\bibitem{b30}
Wikipedia, \url{http://en.wikipedia.org/wiki/Distributed_hash_table}

\bibitem{b31}
Castro, Miguel, et al. "Exploiting network proximity in distributed hash tables." International Workshop on Future Directions in Distributed Computing (FuDiCo). 2002.

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{picture}}]{John Doe}
\blindtext
\end{IEEEbiography}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2014-05-29 execute.sh

@@ -6,7 +6,4 @@
 #   bash execute.sh "uptime"
 
 
-while read IP; do
-    echo "Querying $IP ..." 1>&2
-    ssh -o stricthostkeychecking=no root@$IP "$1" 2> /dev/null &
-done
+

### 2014-05-29 paper.tex
updated paper

@@
 Figure \ref{fig:exp1,1-ids1-cache0} shows an steady average of 6 hops, a value very close to the network mean 7.5.
-This is because nodes perform queries to random buckets, and because we have an average of less than one node per bucket $26/160$, there is no chance for the routing policy to perform any kind of selection based on RTT measurements.
+This is because nodes perform queries to random buckets, and because we have an average of less than one node per bucket $26/160$, there is little chance for the routing policy to perform selection based on RTT measurements, only the farthest buckets from each node ID has several competing routing nodes.
 

### 2014-05-29 paper.tex
updated paper

@@
 
-Distributed Hash Tables (DHT), is a well known and mature decentralized key-value store system.
+Distributed Hash Tables (DHT) is a well known and mature decentralized key-value store system.
 Mainline DHT, the larger DHT deployed world-wide, is commonly used for storing BitTorrent peers, but it works for arbitrary data as well.
@@
 The node IDs are assigned in a manner that ensures that nodes that are close in the network topology are close in the node ID space.
-Geographic Layout was explored as one technique to improve routing performance in CAN \cite{b4}.
+\textit{Geographic Layout} was explored as one technique to improve routing performance in CAN \cite{b4}.
 In one implementation, nodes measure the RTT between themselves and a set of landmark servers to compute the coordinates of the node in the CAN space.
@@
 
-In figure \ref{fig:exp1-ids1-cache100} we see how caching seems to makes convergence to a better locality value, but repetitions of this same experiments shown mixed results.
+In figure \ref{fig:exp1-ids1-cache100} we see how caching seems to makes convergence to a better locality value, but repetitions of this same experiments show mixed results.
 At this point we are not able to conclude that caching leads to better locality, at least in our 26 node DHT.
@@
 
-All node's 120 most significant bits are the same, also an infohash with the same characteristics is inserted in the DHT and all the nodes perform periodic \texttt{GET\_PEERS} requests of this infohash.
+All node's ID 120 most significant bits are the same, also an infohash with the same characteristics is inserted in the DHT and all the nodes perform periodic \texttt{GET\_PEERS} requests of this infohash.
 
@@
 
-This experiment also uses crafted node IDs to force all node's ID being in the same bucket, from the lonely node point of view.
+This experiment also uses crafted node IDs to force all node's ID being in the same bucket from the lonely node point of view.
 We want to create a lot of bucket competition on the lonely node routing table and validate that the physically nearest node is always chosen.
@@
 
-The lonely node is selected from this cluster since it will have plenty of nearby candidates to choose from.
-Figure \ref{fig:exp2,2-cache100-node39-original} illustrates the results of this experiment.
+The lonely node is selected from this cluster since it have plenty of nearby candidates to choose from. Figure \ref{fig:exp2,2-cache100-node39-original} illustrates the results of this experiment.
 
@@
 Solely using the average number of hops may not be a good enough locality evaluator.
-A better one could be the average number of hops of the routing entries over the average number of hops to other nodes, ($\frac{avg(routing\_hops)}{avg(total\_hops}$), or even better, the potential optimal value over the current value.
-In short, making the values dependent of each node will give a better fit.
+A better one could be the average number of hops of the routing entries over the average number of hops to other nodes, ($\frac{avg(routing\_hops)}{avg(total\_hops}$).
+Or even better, the potential optimal value over the current value.
+In short, making the values dependent of each node vision of the network will give a better fit.
 

### 2014-05-29 paper.tex
updated paper

@@
 \section{Conclusion}
-In this paper we have shown that locality in Mainline DHT can be achieved with a very simple routing policy bases on \textit{Proximity Neighbour Selection} with RTT measurements.
+In this paper we have shown that locality in Mainline DHT can be achieved with a very simple routing policy based on \textit{Proximity Neighbour Selection} with RTT measurements.
 We also show that Mainline DHT, as defined in BEP5, is designed specifically for Internet scale deployments, changes on the DHT dimensions are required in order to properly accommodate smaller deployments, for instance, thus on Community Networks.

### 2014-05-29 paper.tex
updated paper

@@
 
-We consider this study very preliminary, further evaluations, with more powerful statistical analysis and more nodes, are needed in order to better quantify the locality properties and their performance implications.
+We consider this study very preliminary, further studies, with more powerful statistical analysis and more nodes, are needed in order to better quantify the locality properties and their performance implications.
 
